### 2023-02-15 Outputs/Paper/paper.qmd
initial commit

---
title: "The Rising Return to Non Cognitive Skill"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

You can and should cross-reference sections and sub-sections. For instance, @sec-data and @sec-first-point.

# Data {#sec-data}

Our data is of penguins (@fig-bills).

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

Also bills and their average (@fig-billssssss). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work.)

```{r}
#| label: fig-billssssss
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk way more about it.

# Model

$$
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}
$$ {#eq-bayes}

@eq-bayes seems useful, eh?

Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful.

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional details

\newpage

# References

### 2023-02-16 Scripts/00-simulate_data.R
update scripts: stimulation,data cleaning and data test done

@@ -1,19 +1,49 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Data: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Simulates The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying
+# Author: Annie Yan, Will Davidson, Jason Ngo
+# Data: 15 February 2023 
+# Contact: yanzixin0807@gmail.com
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: None
+# Any other information needed? None
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+
 
 #### Simulate data ####
-# [...ADD CODE HERE...]
+set.seed(853)
 
+simulated_bullying_data <-
+  tibble(
+    Date = rep(x = as.Date("2021-01-01") + c(0:364), times = 3),
+    
+    State = c(
+      rep(x = "AK", times = 365),
+      rep(x = "CA", times = 365),
+      rep(x = "NY", times = 365)
+    ),
+    
+    Cyberbullying =
+      rpois(
+        n = 365 * 3,
+        lambda = 10
+      ),
+    
+    Schoolbullying =
+      rpois(
+        n = 365 * 3,
+        lambda = 20
+      ),
 
+    School_cyber_bullying =
+      rpois(
+        n = 365 * 3,
+        lambda = 80
+      )
+    
+    )
+    
 
+head(simulated_bullying_data)

### 2023-02-16 Scripts/01-download_data.R

@@ -1,26 +1,26 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Data: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: read and saves the data from server
+# Author: Annie Yan, Will Davidson, Jason Ngo
+# Data: 15 February 2023 
+# Contact: yanzixin0807@gmail.com
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
+# Pre-requisites: None
+# Any other information needed? None
 
 #### Workspace setup ####
-library(opendatatoronto)
 library(tidyverse)
+library(haven)
 # [...UPDATE THIS...]
 
 #### Download data ####
 # [...ADD CODE HERE TO DOWNLOAD...]
 
+raw_data <- read_dta('/Users/annie/Desktop/Spring 2023/Worlds become data/Analysis on The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying/draft/data/analysis_file.dta')
 
 
 #### Save data ####
 # [...UPDATE THIS...]
 # change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(the_raw_data, "inputs/data/raw_data.csv") 
+write_csv(raw_data, "inputs/data/raw_data.csv") 
 
          

### 2023-02-16 Scripts/02-data_cleaning.R

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Cleans.... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Data: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans raw data
+# Author: Annie Yan, Will Davidson, Jason Ngo
+# Data: 15 February 2023 
+# Contact: yanzixin0807@gmail.com
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: None
+# Any other information needed? None
 
 
 #### Workspace setup ####
@@ -16,7 +16,11 @@ library(tidyverse)
 # [...UPDATE THIS...]
 raw_data <- read_csv("inputs/data/raw_data.csv")
 
-
+cleaned_data <- 
+  raw_data |> select (state,date,year,month,
+                      cy_bly,sch_bly,sch_cy_bly,sch_cy_bly_sum,
+                      yrbs_bly_sch,yrbs_bly_cyb,yrbs_bly_avg,
+                      avg_t,avg_v,pop2019)
 
 
 #### Save data ####

### 2023-02-16 Scripts/04-test_data.R

@@ -1,11 +1,11 @@
 #### Preamble ####
 # Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Data: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Author: Annie Yan, Will Davidson, Jason Ngo
+# Data: 15 February 2023 
+# Contact: yanzixin0807@gmail.com
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: None
+# Any other information needed? None
 
 
 #### Workspace setup ####
@@ -13,3 +13,7 @@ library(tidyverse)
 # [...UPDATE THIS...]
 
 #### Test data ####
+
+cleaned_data$date  |> class() == "Date"
+cleaned_data$ cy_bly |> min(na.rm=TRUE) >= 0
+cleaned_data$ sch_cy_bly|> max(na.rm=TRUE) <= 240 

### 2023-02-16 Scripts/04-test_data.R
update scripts

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
+# Purpose: Tests cleaned data
 # Author: Annie Yan, Will Davidson, Jason Ngo
 # Data: 15 February 2023 
 # Contact: yanzixin0807@gmail.com
@@ -10,7 +10,7 @@
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+
 
 #### Test data ####
 

### 2023-02-17 Scripts/01-download_data.R
Updated download file

@@ -1,26 +1,29 @@
 #### Preamble ####
-# Purpose: read and saves the data from server
+# Purpose: Read and Locally Save the Downloaded Data
 # Author: Annie Yan, Will Davidson, Jason Ngo
 # Data: 15 February 2023 
 # Contact: yanzixin0807@gmail.com
 # License: MIT
-# Pre-requisites: None
+# Pre-requisites: An account on ICPSR
 # Any other information needed? None
 
 #### Workspace setup ####
 library(tidyverse)
 library(haven)
-# [...UPDATE THIS...]
 
 #### Download data ####
-# [...ADD CODE HERE TO DOWNLOAD...]
+#Code is manually downloaded from https://www.openicpsr.org/openicpsr/project/156901/version/V1/view
+#To download, please login with an existing ICPSR account or register a new account
 
-raw_data <- read_dta('/Users/annie/Desktop/Spring 2023/Worlds become data/Analysis on The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying/draft/data/analysis_file.dta')
-
+#raw_data <- read_dta('/Users/annie/Desktop/Spring 2023/Worlds become data/Analysis on The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying/draft/data/analysis_file.dta')
 
 #### Save data ####
-# [...UPDATE THIS...]
-# change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(raw_data, "inputs/data/raw_data.csv") 
+# Locally save the downloaded data in the project space
+Unclean_data <- read.csv(here::here("Inputs/data/raw_data.csv"))
+state_bully_data <- read.csv(here::here("Inputs/data/2021_03_30_monthly_2012_2021_state_bullying_topic.csv"))
+state_cybully_data <- read.csv(here::here("Inputs/data/2021_03_30_monthly_2012_2021_state_cyb_bullying_topic.csv"))
+state_schbully_data <- read.csv(here::here("Inputs/data/2021_03_30_monthly_2012_2021_state_sch_bullying_topic.csv"))
+
+#write_csv(raw_data, "inputs/data/raw_data.csv") 
 
          

### 2023-02-17 Scripts/01-download_data.R
Cleaned Data and Saves It

@@ -23,7 +23,7 @@ Unclean_data <- read.csv(here::here("Inputs/data/raw_data.csv"))
 state_bully_data <- read.csv(here::here("Inputs/data/2021_03_30_monthly_2012_2021_state_bullying_topic.csv"))
 state_cybully_data <- read.csv(here::here("Inputs/data/2021_03_30_monthly_2012_2021_state_cyb_bullying_topic.csv"))
 state_schbully_data <- read.csv(here::here("Inputs/data/2021_03_30_monthly_2012_2021_state_sch_bullying_topic.csv"))
-
+demographic_data <- read.csv(here::here("Inputs/data/sc-est2019-agesex-civ.csv"))
 #write_csv(raw_data, "inputs/data/raw_data.csv") 
 
          

### 2023-02-17 Scripts/02-data_cleaning.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Cleans raw data
+# Purpose: Cleans raw data by selecting relevant data
 # Author: Annie Yan, Will Davidson, Jason Ngo
 # Data: 15 February 2023 
 # Contact: yanzixin0807@gmail.com
@@ -14,17 +14,78 @@ library(tidyverse)
 
 #### Clean data ####
 # [...UPDATE THIS...]
-raw_data <- read_csv("inputs/data/raw_data.csv")
+#raw_data <- read_csv("inputs/data/raw_data.csv")
 
-cleaned_data <- 
-  raw_data |> select (state,date,year,month,
-                      cy_bly,sch_bly,sch_cy_bly,sch_cy_bly_sum,
-                      yrbs_bly_sch,yrbs_bly_cyb,yrbs_bly_avg,
-                      avg_t,avg_v,pop2019)
+#cleaned_data <- 
+#  raw_data |> select (state,date,year,month,
+#                      cy_bly,sch_bly,sch_cy_bly,sch_cy_bly_sum,
+#                      yrbs_bly_sch,yrbs_bly_cyb,yrbs_bly_avg,
+#                      avg_t,avg_v,pop2019)
 
+#Filter by states with the 10 highest Asian Populations
+#California, New York, Texas, New Jersey, Washington
+#Illinois, Hawaii, Florida, Virginia, Massachusetts
+state_bully_data <- state_bully_data |> filter(dma_json_code == 'US-CA' | dma_json_code == 'US-NY' | dma_json_code == 'US-TX' |
+                                                    dma_json_code == 'US-NJ' | dma_json_code == 'US-WA' | dma_json_code == 'US-IL' |
+                                                    dma_json_code == 'US-HI' | dma_json_code == 'US-FL' | dma_json_code == 'US-VA' |
+                                                    dma_json_code == 'US-MA', na.rm = TRUE)
 
+state_cybully_data <- state_cybully_data |> filter(dma_json_code == 'US-CA' | dma_json_code == 'US-NY' | dma_json_code == 'US-TX' |
+                                                 dma_json_code == 'US-NJ' | dma_json_code == 'US-WA' | dma_json_code == 'US-IL' |
+                                                 dma_json_code == 'US-HI' | dma_json_code == 'US-FL' | dma_json_code == 'US-VA' |
+                                                 dma_json_code == 'US-MA', na.rm = TRUE)
+
[…]

### 2023-02-17 Outputs/Paper/paper.qmd
Cleaning, graph data
more cleaning, separating dates. more csv's solely for graphing

@@
 You can and should cross-reference sections and sub-sections. For instance, @sec-data and @sec-first-point.
+
+talking points
+1) why asian population? because anti-asian violence in the usa grew. we want to see if anti-asian violence was also reflected in school and cyber bullying (introduction).
+2) our replicated graphs show that bullying numbers dropped during covid, 
+3) But there wasnt a significant correlation between asian population of states and school bullying numbers
+4) do a comparison of top 10 asian vs bottom 10 asian population states to see if asian population actually matters in school bullying
+5) lack of correlation testing, this is only reported bullying, not reflected of everyone getting bullied. only those that search
+6) next steps: try asian population in certain schools instead of states? a hard comparison between asian bullying and violence?
+7) bias of only reported data (sampling) with people that only searches for bullying.
+ethics of using peoples search data.
+unreliability of measurement.
+not every1 uses google for searches or bullying help.
+google's algorithm will shift towards anti-bullying stuff for people that search for it.
+
+```{r}
+#### use this code to graph the 3 bully datas
+
+#state_bully_data |> ggplot(aes(x = date, y = sum)) + 
+ # geom_col() +
+  #theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  #labs(
+  #  x = "School Year Date Intervals",
+  #  y = "Sum of Searches by Investigated States"
+  #)
+
+```
 

### 2023-02-17 Scripts/02-data_cleaning.R

@@ -84,8 +84,37 @@ state_schbully_data <- state_schbully_data |> mutate(State.Name=recode(State.Nam
                                                                  'US-FL' = 'Florida',
                                                                  'US-VA' = 'Virginia',
                                                                  'US-MA' = 'Massachusetts'))
+#Separating the dates to filter them
+state_bully_data <- state_bully_data |> mutate(year = lubridate::year(date), 
+                                                   month = lubridate::month(date), 
+                                                   day = lubridate::day(date))
+state_cybully_data <- state_cybully_data |> mutate(year = lubridate::year(date), 
+                                               month = lubridate::month(date), 
+                                               day = lubridate::day(date))
+state_schbully_data <- state_schbully_data |> mutate(year = lubridate::year(date), 
+                                               month = lubridate::month(date), 
+                                               day = lubridate::day(date))
+
+#Selecting Jan, Mar, Jul & Sep as they represent 3 months of a school year and one summer month
+state_bully_data <- state_bully_data |> filter(month == 1 | month == 7 | month == 9 | month == 3)
+state_cybully_data <- state_cybully_data |> filter(month == 1 | month == 7 | month == 9 | month == 3)
+state_schbully_data <- state_schbully_data |> filter(month == 1 | month == 7 | month == 9 | month == 3)
+
+
+#Using data from 2016 and above
+state_bully_data <- state_bully_data |> filter(year > 2015)
+state_cybully_data <- state_cybully_data |> filter(year > 2015)
+state_schbully_data <- state_schbully_data |> filter(year > 2015)
+
+#Summarized sum by the 4 months, saved in another variable that'll solely be used to graph
+state_bully_data_sum <- state_bully_data|>group_by(date)|>summarise(sum = sum(hits))
+state_cybully_data_sum <- state_cybully_data|>group_by(date)|>summarise(sum = sum(hits))
+state_schbully_data_sum <- state_schbully_data|>group_by(date)|>summarise(sum = sum(hits))
+
 #### Save data ####
 write.csv(state_bully_data, here::here("Outputs/data/cleaned_bully_data.csv"))
 write.csv(state_cybully_data, here::here("Outputs/data/cleaned_cybully_data.csv"))
 write.csv(state_schbully_data, here::here("Outputs/data/cleaned_schbully_data.csv"))
-
+write.csv(state_bully_data_sum, here::here("Outputs/data/sum_bully_data.csv"))
[…]

### 2023-02-17 Outputs/Paper/paper.qmd
split work, add graphs, lubridate
split writing work amongst us, added the 3 replicated graphs on quarto, added lubridate library

--- 2023-02-15 Outputs/Paper/paper.qmd
@@
 library(tidyverse)
-library(palmerpenguins)
+
+sum_bully_data <- read.csv(here::here("Outputs/data/sum_bully_data.csv"))
+sum_cybully_data <- read.csv(here::here("Outputs/data/sum_cybully_data.csv"))
+sum_schbully_data <- read.csv(here::here("Outputs/data/sum_schbully_data.csv"))
 ```
@@
 You can and should cross-reference sections and sub-sections. For instance, @sec-data and @sec-first-point.
+
+talking points
+1) why asian population? because anti-asian violence in the usa grew. we want to see if anti-asian violence was also reflected in school and cyber bullying (introduction). (will)
+
+2) our replicated graphs show that bullying numbers dropped during covid, (wil)
+
+3) But there wasnt a significant correlation between asian population of states and school bullying numbers (annie)
+
+4) do a comparison of top 10 asian vs bottom 10 asian population states to see if asian population actually matters in school bullying (jason)
+
+5) lack of correlation testing, this is only reported bullying, not reflected of everyone getting bullied. only those that search (annie)
+
+6) next steps: try asian population in certain schools instead of states? a hard comparison between asian bullying and violence? (annie)
+
+7) bias of only reported data (sampling) with people that only searches for bullying.
+ethics of using peoples search data.
+unreliability of measurement.
+not every1 uses google for searches or bullying help.
+google's algorithm will shift towards anti-bullying stuff for people that search for it.
+(will)
+
+```{r}
+#| label: bullydata
+#| fig-cap: 3 graphs lol
+#| echo: false
+#| warning: false
+
+#### use this code to graph the 3 bully datas ####
+
+sum_bully_data |> ggplot(aes(x = date, y = sum)) + 
+  geom_col() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  labs(
+    title = "Sum of All Bullying",
+    x = "School Year Date Intervals",
+    y = "Sum of Searches by Investigated States"
+  )
+sum_cybully_data |> ggplot(aes(x = date, y = sum)) + 
+  geom_col() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  labs(
+    title = "Sum of Cyberbullying",
+    x = "School Year Date Intervals",
+    y = "Sum of Searches by Investigated States"
+  )
+sum_schbully_data |> ggplot(aes(x = date, y = sum)) + 
+  geom_col() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  labs(
+    title = "Sum of School Bullying",
+    x = "School Year Date Intervals",
+    y = "Sum of Searches by Investigated States"
+  )
+
+```
 

### 2023-02-17 Scripts/02-data_cleaning.R

@@ -10,6 +10,7 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(lubridate)
 # [...UPDATE THIS...]
 
 #### Clean data ####

### 2023-02-17 Scripts/05-testing_graphs.R

@@ -1,0 +1,38 @@
+state_bully_data |> ggplot(aes(x = date, y = hits, color = State.Name)) + geom_point() + theme(axis.text.x = element_text(angle = 45,hjust=1))
+bully_dates_test <- state_bully_data %>% mutate(year = lubridate::year(date), 
+                      month = lubridate::month(date), 
+                      day = lubridate::day(date))
+bully_dates_test <- bully_dates_test |> filter(month == 1 | month == 7)
+bully_dates_test <- bully_dates_test |> filter(year > 2015)
+
+bully_dates_test_2 <- bully_dates_test|>group_by(date)|>summarise(sum = sum(hits))
+
+bully_dates_test |> ggplot(aes(x = date, y = hits)) + 
+  geom_point(size = 3, alpha = 0.5) + 
+  geom_line() + 
+  theme(axis.text.x = element_text(angle = 45,hjust=1))
+
+bully_dates_test_2 |> ggplot(aes(x = date, y = sum)) + 
+  geom_col() + 
+  theme(axis.text.x = element_text(angle = 45,hjust=1))
+
+state_bully_data_2 <- state_bully_data_2 |> filter(dma_json_code == 'US-CA' | dma_json_code == 'US-NY' | dma_json_code == 'US-TX' |
+                                                 dma_json_code == 'US-NJ' | dma_json_code == 'US-WA' | dma_json_code == 'US-IL' |
+                                                 dma_json_code == 'US-HI' | dma_json_code == 'US-FL' | dma_json_code == 'US-VA' |
+                                                 dma_json_code == 'US-MA', na.rm = TRUE)
+
+state_bully_data_2 <- state_bully_data_2 |> mutate(year = lubridate::year(date), 
+                                                month = lubridate::month(date), 
+                                                day = lubridate::day(date))
+
+state_bully_data_2 <- state_bully_data_2 |> filter(month == 1 | month == 7 | month == 9 | month == 3)
+state_bully_data_2 <- state_bully_data_2 |> filter(year > 2015)
+state_bully_data_2 <- state_bully_data_2|>group_by(date)|>summarise(sum = sum(hits))
+
+state_bully_data |> ggplot(aes(x = date, y = sum)) + 
+  geom_col() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  labs(
+    x = "School Year Date Intervals",
+    y = "Sum of Searches by Investigated States"
+  )

### 2023-02-17 Outputs/Paper/paper.qmd
updated graphs a bit

@@
 
+library(tidyverse)
+
 #### use this code to graph the 3 bully datas ####
@@
   geom_col() +
-  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black")) +
   labs(
-    title = "Sum of All Bullying",
-    x = "School Year Date Intervals",
-    y = "Sum of Searches by Investigated States"
+    title = "All 'Bullying' Searches in High Asian Population States",
+    x = "Date",
+    y = "Total Searches"
   )
@@
   geom_col() +
-  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black")) +
   labs(
-    title = "Sum of Cyberbullying",
-    x = "School Year Date Intervals",
-    y = "Sum of Searches by Investigated States"
+    title = "'Cyberbullying' Searches in High Asian Population States",
+    x = "Date",
+    y = "Total Searches"
   )
@@
   geom_col() +
-  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black")) +
   labs(
-    title = "Sum of School Bullying",
-    x = "School Year Date Intervals",
-    y = "Sum of Searches by Investigated States"
+    title = "'School Bullying' Searches in High Asian Population States",
+    x = "Date",
+    y = "Total Searches"
   )

### 2023-02-20 Outputs/Paper/paper.qmd
Update paper qmd, adding dataset

--- 2023-02-17 Outputs/Paper/paper.qmd
@@
 ---
-title: "The Rising Return to Non Cognitive Skill"
+title: "Analysis on The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying"
 subtitle: "My subtitle if needed"
 author: 
-  - First author
-  - Another author
-thanks: "Code and data are available at: LINK."
+  - Will Davidson
+  - Jason Ngo
+  - Annie Yan
+thanks: "Code and data are available at: https://github.com/AnnieYan0807/Analysis-on-The-COVID-19-Pandemic-Disrupted-Both-School-Bullying-and-Cyberbullying."
 date: "`r Sys.time()`"
@@
 
+# read cleaned data
 library(tidyverse)
@@
 sum_schbully_data <- read.csv(here::here("Outputs/data/sum_schbully_data.csv"))
+
+cleaned_bully_data <- read.csv(here::here("Outputs/data/cleaned_schbully_data.csv"))
+cleaned_cybully_data <- read.csv(here::here("Outputs/data/cleaned_schbully_data.csv"))
+cleaned_schbully_data <- read.csv(here::here("Outputs/data/cleaned_schbully_data.csv"))
+
+# read nationwide data for discussion point 2
+sum_national_schbully_data <- read.csv(here::here("Outputs/data/sum_national_schbully_data.csv"))
 ```
@@
 
-talking points
-1) why asian population? because anti-asian violence in the usa grew. we want to see if anti-asian violence was also reflected in school and cyber bullying (introduction). (will)
+talking points 1) why asian population? because anti-asian violence in the usa grew. we want to see if anti-asian violence was also reflected in school and cyber bullying (introduction). (will)
 
@@
 
+library(tidyverse)
+
 #### use this code to graph the 3 bully datas ####
 
-sum_bully_data |> ggplot(aes(x = date, y = sum)) + 
+cleaned_bully_data |> ggplot(aes(x = date, 
+                                    y = hits,
+                                    fill = State.Name)) + 
   geom_col() +
-  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 8)) +
   labs(
-    title = "Sum of All Bullying",
-    x = "School Year Date Intervals",
-    y = "Sum of Searches by Investigated States"
+    title = "All 'Bullying' Searches in High Asian Population States",
+    x = "Date",
+    y = "Search Frequency",
+    fill = "State Name"
   )
-sum_cybully_data |> ggplot(aes(x = date, y = sum)) + 
+
+cleaned_cybully_data |> ggplot(aes(x = date, 
+                                    y = hits,
+                                    fill = State.Name)) + 
   geom_col() +
-  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 8)) +
   labs(
-    title = "Sum of Cyberbullying",
-    x = "School Year Date Intervals",
-    y = "Sum of Searches by Investigated States"
+    title = "'Cyberbullying' Searches in High Asian Population States",
+    x = "Date",
+    y = "Search Frequency",
+    fill = "State Name"
   )
-sum_schbully_data |> ggplot(aes(x = date, y = sum)) + 
+
+cleaned_schbully_data |> ggplot(aes(x = date, 
+                                    y = hits,
+                                    fill = State.Name)) + 
   geom_col() +
-  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 8)) +
   labs(
-    title = "Sum of School Bullying",
-    x = "School Year Date Intervals",
-    y = "Sum of Searches by Investigated States"
+    title = "'School Bullying' Searches in High Asian Population States",
+    x = "Date",
+    y = "Search Frequency",
+    fill = "State Name"
   )
@@
 
-# Data {#sec-data}
+# Data
 
-Our data is of penguins (@fig-bills).
+## Data collection
 
-```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
-#| echo: false
-
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
-```
-
-Talk more about it.
-
-Also bills and their average (@fig-billssssss).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work.)
-
-```{r}
-#| label: fig-billssssss
-#| fig-cap: More bills of penguins
-#| echo: false
-#| fig-width: 8
-#| fig-height: 4
-
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
-```
-
-Talk way more about it.
-
-# Model
-
-$$
-Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}
-$$ {#eq-bayes}
-
-@eq-bayes seems useful, eh?
-
-Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR].
-We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful.
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
+## Measurements
 
@@
 
-## First discussion point {#sec-first-point}
+## First discussion point
 
@@
 
-## Second discussion point
+## Correlation between asian population of states and school bullying numbers
+
+As discussed earlier, there has been a significant increase in anti-Asian culture in the United States over the past year.
+Many may be attributed to the spread of misinformation and xenophobic rhetoric related to the COVID-19 pandemic, which has stoked hatred against Asian communities.
+Reports show that 81% of Asian adults state violence against them is increasing.
+Over 3800 hate-related verbal and physical assaults against Asian Americans have been reported during the pandemic.
+
+This culture of anti-Asian violence has also impacted schools, with many Asian students reporting incidents of racism and discrimination in the classroom.
+Reports show 68% of attacks were verbal harassment.
+Some students may have faced racially discriminated comments, while others may have experienced exclusion or isolation from their peers.
+These reports have drawn our attention.
+We are eager to learn if there is a need to increase education and awareness among students, as well as efforts to combat racism and discrimination in all forms.
+
+We conducted a study to determine if there was a correlation between the increasing anti-Asian sentiment and school bullying in the United States.
+To do this, we analyzed the correlation between the search frequency for the term "school bullying" and the Asian population of each state.
+Figures 2 and 3 were used to compare the search frequency of the keyword "school bullying" and the date.
+
+```{r}
+#| label: School bullying searches in top 10 states with highest asian population
+#| fig-cap: School bullying searches in top 10 states with highest asian population
+#| echo: false
+#| warning: false
+
+library(tidyverse)
+
+cleaned_schbully_data |> ggplot(aes(x = date, 
+                                    y = hits,
+                                    fill = State.Name)) + 
+  geom_col() +
+  labs(
+    title = "'School Bullying' Searches in High Asian Population States",
+    x = "Date",
+    y = "Search Frequency",
+    fill = "State Name",
+    cex.fill = 1
+    )+
+    theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 8) ) 
+```
+
+Figure 2 shows the frequency of the keyword "school bullying" searched online within the top ten states with the highest Asian population.
+The graph indicates that March 1st, 2018, had the highest number of searches for "school bullying" at over 400.
+Typically, the search frequency for "school bullying" is highest in March, and there is a significant drop in search frequency every July at approximately 150 searches when summer vacation is halfway through.
+In contrast, data for September and January are relatively closer to the average, ranging from 150 to 300.
+
+```{r}
+#| label: School bullying searches nationwide
+#| fig-cap: School bullying searches nationwide
+#| echo: false
+#| warning: false
+
+library(tidyverse)
+
+sum_national_schbully_data |> ggplot(aes(x = date, y = sum)) + 
+  geom_col() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black")) +
+  labs(
+    title = "'School Bullying' Searches Nationwide",
+    x = "Date",
+    y = "Search Frequency"
+  )
+
+```
+
+Figure 3 presents data on the search frequency of the keyword "school bullying" nationally since 2016.
+Like Figure 2, March 1st, 2018, had the highest search frequency at 2000 nationally.
+On the other hand, July's search frequency was always at the lowest level, with data from 2016 to 2021 never exceeding 750.
+September and January have a similar level of search frequency ranging from 750 to 1500, which is closer to the overall average.
+In terms of trends, the search frequency with respect to date was relatively consistent in both the top ten states with the highest Asian population and nationwide.
+Based on our analysis, we did not find a correlation between school bullying searches and the Asian population of the state.
+
+Upon comparing Figure 2 and Figure 3, we observed a consistent trend.
+Notably, the months of January and September, which mark the beginning of school, exhibit comparable search frequency levels for the keyword "school bullying." Meanwhile, March, which falls in the middle of the semester, experiences a significant surge in search frequency, as seen in both national data and the top ten states with the highest Asian population.
+On the other hand, July, which is in the middle of summer break, displays a considerable drop in search frequency in both graphs.
+Overall, the trend in search frequency with respect to date remains relatively consistent across the top ten states with the highest Asian population and the entire nation.
+Therefore, the comparison of these two graphs did not establish any significant correlation.
+
+In summary, by comparing trends in two graphs, our investigation did not reveal any correlation between the Asian population of a state and the frequency of searches related to school bullying.
+While anti-Asian culture is still a large concern in the U.S., it does not seem to have a direct impact on school bullying.
+It is possible that factors like school policies, awareness campaigns, and changes in social media usage have made a positive impact on preventing discrimination and stereotyping from happening.
 
@@
 
-## Weaknesses and next steps
+## Weaknesses
 
-Weaknesses and next steps should also be included.
+While our study provides some insights into the search frequency of school bullying and its correlation with the Asian population, it has several limitations.
+Firstly, we only looked at the search frequency of the keyword "school bullying" and did not consider other related search terms or social media platforms, which may not fully capture the prevalence of school bullying in schools.
+Secondly, we did not control for other variables, such as socioeconomic status, which may also impact the prevalence of school bullying.
+Lastly, as we only analyzed data up until 2021, our study may not reflect any potential changes in search behavior or trends in recent months or years.
+These limitations should be taken into consideration when interpreting our findings and drawing conclusions.
 
-\newpage
+Furthermore, we did not perform any correlation testing to establish a relationship between the Asian population and the search frequency of "school bullying" accurately.
+We simply compared the search frequency of the top ten states with the highest Asian population and nationwide data.
+To determine if there is a statistically significant relationship between the two variables, a formal correlation test is required.
+However, it is also important to note that correlation does not mean causation.
+Even if the search frequency of "school bullying" and the Asian population in a state are significantly correlated, it does not imply that the increasing incidence of school bullying is caused by a high Asian population or that anti-Asian culture impacts school campuses.
+Other factors, such as confounding variables or common causes, may influence the observed relationship.
+As a result, further studies are needed to examine the impact of anti-Asian culture on school bullying.
 
-\appendix
+In conclusion, our study has some limitations that should be taken into account when interpreting our results.
+Although we provide some insights into the correlation between the Asian population and the search frequency of "school bullying," future research is required to investigate the potential causes of school bullying, particularly those related to anti-Asian culture.
 
-# Appendix {-}
+## Next steps
 
-# Additional details
+As discussed above, further studies are crucial for our studies.
+Some potential steps include establishing more in-depth data analysis, adding more control variables, and conducting formal correlation tests.
+To establish a more in-depth data analysis on school bullying and its relationship with the Asian population, we suggest introducing more factors that relate to school bullying, such as other related search terms and various social media, to provide a more complete picture of the issue.
+Adding more control variables is another direction to further testing school bullying and its relationship with the Asian population.
+Age range, race, gender, or even socioeconomic status all can influence school bullying.
+Taking these factors into consideration can help us to identify potential areas for intervention.
+Furthermore, it is important to conduct formal correlation tests to determine the statistical significance of the relationship between school bullying and the Asian population.
+Gathering more data, such as Asian population in different states, can be helpful in this regard.
+The correlation coefficient can be calculated to determine the strength and direction of the relationship between the two variables.
+Besides, additional research is necessary to identify the underlying factors driving the relationship between school bullying and the Asian population.
+
+## Bias
 

### 2023-02-20 Outputs/Paper/starter folder draft.R

@@ -1,0 +1,23 @@
+###draft
+
+Our data is of penguins (@fig-bills).
+
+Talk more about it.
+
+Also bills and their average (@fig-billssssss). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work.)
+
+
+Talk way more about it. 
+
+
+# Model
+
+$$
+  Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}
+  $$ {#eq-bayes}
+    
+    @eq-bayes seems useful, eh?
+      
+      Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful. 
+
+We can use maths by including latex between dollar signs, for instance $\theta$.

### 2023-02-20 Scripts/02-data_cleaning.R

@@ -15,13 +15,25 @@ library(lubridate)
 
 #### Clean data ####
 # [...UPDATE THIS...]
-#raw_data <- read_csv("inputs/data/raw_data.csv")
 
-#cleaned_data <- 
-#  raw_data |> select (state,date,year,month,
-#                      cy_bly,sch_bly,sch_cy_bly,sch_cy_bly_sum,
-#                      yrbs_bly_sch,yrbs_bly_cyb,yrbs_bly_avg,
-#                      avg_t,avg_v,pop2019)
+##National wide data##
+#create new dataset: national schbully data 
+national_schbully_data <- state_schbully_data
+national_schbully_data <- national_schbully_data |> mutate(keyword=recode(keyword, '%2Fm%2F03m50g4' = 'School Bullying'))
+national_schbully_data <- national_schbully_data |> rename(Location = dma_json_code)
+national_schbully_data <- national_schbully_data |> mutate(year = lubridate::year(date), 
+                                                     month = lubridate::month(date), 
+                                                     day = lubridate::day(date))
+national_schbully_data <- national_schbully_data |> filter(month == 1 | month == 7 | month == 9 | month == 3)
+national_schbully_data <- national_schbully_data |> filter(year > 2015)
+national_schbully_data_sum <- national_schbully_data|>group_by(date)|>summarise(sum = sum(hits))
+write.csv(national_schbully_data_sum, here::here("Outputs/data/sum_national_schbully_data.csv"))
+write.csv(national_schbully_data, here::here("Outputs/data/cleaned_national_schbully_data.csv"))
+
+
+
+
+## Top 10 states with highest asian population ##
 
 #Filter by states with the 10 highest Asian Populations
 #California, New York, Texas, New Jersey, Washington
@@ -111,6 +123,7 @@ state_schbully_data <- state_schbully_data |> filter(year > 2015)
 state_bully_data_sum <- state_bully_data|>group_by(date)|>summarise(sum = sum(hits))
 state_cybully_data_sum <- state_cybully_data|>group_by(date)|>summarise(sum = sum(hits))
 state_schbully_data_sum <- state_schbully_data|>group_by(date)|>summarise(sum = sum(hits))
+
 
 #### Save data ####
 write.csv(state_bully_data, here::here("Outputs/data/cleaned_bully_data.csv"))

### 2023-02-21 Scripts/04-test_data.R
update paper

@@ -12,8 +12,60 @@
 library(tidyverse)
 
 
+sum_bully_data <- read.csv(here::here("Outputs/data/sum_bully_data.csv"))
+sum_cybully_data <- read.csv(here::here("Outputs/data/sum_cybully_data.csv"))
+sum_schbully_data <- read.csv(here::here("Outputs/data/sum_schbully_data.csv"))
+sum_national_schbully_data <- read.csv(here::here("Outputs/data/sum_national_schbully_data.csv"))
+
+cleaned_bully_data <- read.csv(here::here("Outputs/data/cleaned_schbully_data.csv"))
+cleaned_cybully_data <- read.csv(here::here("Outputs/data/cleaned_schbully_data.csv"))
+cleaned_schbully_data <- read.csv(here::here("Outputs/data/cleaned_schbully_data.csv"))
+cleaned_national_schbully_data <- read.csv(here::here("Outputs/data/cleaned_national_schbully_data.csv"))
+
+
 #### Test data ####
 
-cleaned_data$date  |> class() == "Date"
-cleaned_data$ cy_bly |> min(na.rm=TRUE) >= 0
-cleaned_data$ sch_cy_bly|> max(na.rm=TRUE) <= 240 
+#cleaned_bully_data
+cleaned_bully_data$ hits  |> class() == "integer"
+cleaned_bully_data$ month |> min(na.rm=TRUE) >= 0
+cleaned_bully_data$ day|> max(na.rm=TRUE) <= 31
+
+#cleaned_cybully_data
+cleaned_cybully_data$ hits  |> class() == "integer"
+cleaned_cybully_data$ month |> min(na.rm=TRUE) >= 0
+cleaned_cybully_data$ day|> max(na.rm=TRUE) <= 31
+
+
+#cleaned_schbully_data
+cleaned_schbully_data$ hits  |> class() == "integer"
+cleaned_schbully_data$ month |> min(na.rm=TRUE) >= 0
+cleaned_schbully_data$ day|> max(na.rm=TRUE) <= 31
+
+#cleaned_national_schbully_data
+cleaned_national_schbully_data$ hits  |> class() == "integer"
+cleaned_national_schbully_data$ month |> min(na.rm=TRUE) >= 0
+cleaned_national_schbully_data$ day|> max(na.rm=TRUE) <= 31
+
+
+#sum_bully_data
+sum_bully_data$ X  |> class() == "integer"
+sum_bully_data$ date  |> class() == "character"
+sum_bully_data$ sum  |> class() == "integer"
+
[…]

### 2023-02-21 Outputs/Paper/paper.qmd
update paper2

@@
 
-cleaned_bully_data |> ggplot(aes(x = date, 
-                                    y = hits,
-                                    fill = State.Name)) + 
+sum_bully_data |> ggplot(aes(x = date, y = sum)) + 
   geom_col() +
@@
 
-cleaned_cybully_data |> ggplot(aes(x = date, 
-                                    y = hits,
-                                    fill = State.Name)) + 
+sum_cybully_data |> ggplot(aes(x = date, y = sum)) + 
   geom_col() +
@@
 
-cleaned_schbully_data |> ggplot(aes(x = date, 
-                                    y = hits,
-                                    fill = State.Name)) + 
+sum_schbully_data |> ggplot(aes(x = date, y = sum)) + 
   geom_col() +

### 2023-02-21 Outputs/Paper/paper.qmd
update paper 3

@@
 
+## Estimand
+In the study, our estimated population vary for different datasets.
+The population of the data used in figures 1, 2, 3, and 4 contains people who live in the top ten states with the highest Asian population.
+These states includes California, Florida, Hawaii, Illinois, Massachusetts, New Jersey, New York, Texas, Virginia, and Washington.
+(@cit3) Nationwide data includes population of all people who live in the United States.
+
 ```{r}
@@
 
+The data used in this study were pulled from reproducible package of article "Data and code for: The COVID-19 pandemic disrupted both school bullying and cyberbullying." (@cit4) According to the article, raw data were provided from Google Trends and Youth Risk Behavior Survey.
+
+To analysis these data, R programing language (@citeR), tidyverse (@citeTidyverse), and dplyr (@citedplyr) are used.
+ggplot2 (@citeggplot2) has been used in order to produce graphic reports.
+The use of knitr (@citeknitr) helped us to generate tables.
+Lubridate (@citelubridate) are used to reformat dates.
+
 ## Measurements
+All the data we used is from after 2016.
+In our study, bullying data includes school bullying data and cyberbullying data.
+We measure the intensity of bullying by number of hits in one day.
+In the paper, we will refer it as search frequency.
 
-# Results
+## Data Analysis
 
-# Discussion
+### bullying number droped after covid
 
-## First discussion point
-
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
-
-## Correlation between asian population of states and school bullying numbers
-
-As discussed earlier, there has been a significant increase in anti-Asian culture in the United States over the past year.
-Many may be attributed to the spread of misinformation and xenophobic rhetoric related to the COVID-19 pandemic, which has stoked hatred against Asian communities.
-Reports show that 81% of Asian adults state violence against them is increasing.
-Over 3800 hate-related verbal and physical assaults against Asian Americans have been reported during the pandemic.
-
-This culture of anti-Asian violence has also impacted schools, with many Asian students reporting incidents of racism and discrimination in the classroom.
-Reports show 68% of attacks were verbal harassment.
-Some students may have faced racially discriminated comments, while others may have experienced exclusion or isolation from their peers.
-These reports have drawn our attention.
-We are eager to learn if there is a need to increase education and awareness among students, as well as efforts to combat racism and discrimination in all forms.
+### Correlation between asian population of states and school bullying numbers
 
@@
 To do this, we analyzed the correlation between the search frequency for the term "school bullying" and the Asian population of each state.
-Figures 2 and 3 were used to compare the search frequency of the keyword "school bullying" and the date.
+Figures 4 and 5 were used to compare the search frequency of the keyword "school bullying" and the date.
 
@@
 #| label: School bullying searches in top 10 states with highest asian population
-#| fig-cap: School bullying searches in top 10 states with highest asian population
+#| fig-cap: "School bullying searches in top 10 states with highest asian population"
 #| echo: false
@@
 
-Figure 2 shows the frequency of the keyword "school bullying" searched online within the top ten states with the highest Asian population.
+Figure 4  shows the frequency of the keyword "school bullying" searched online within the top ten states with the highest Asian population.
 The graph indicates that March 1st, 2018, had the highest number of searches for "school bullying" at over 400.
@@
 
-```{r}
+```{r figure2}
 #| label: School bullying searches nationwide
@@
 
-Figure 3 presents data on the search frequency of the keyword "school bullying" nationally since 2016.
-Like Figure 2, March 1st, 2018, had the highest search frequency at 2000 nationally.
+Figure 5 presents data on the search frequency of the keyword "school bullying" nationally since 2016.
+Like Figure 4, March 1st, 2018, had the highest search frequency at 2000 nationally.
 On the other hand, July's search frequency was always at the lowest level, with data from 2016 to 2021 never exceeding 750.
@@
 
-Upon comparing Figure 2 and Figure 3, we observed a consistent trend.
+Upon comparing Figure 4 and Figure 5, we observed a consistent trend.
 Notably, the months of January and September, which mark the beginning of school, exhibit comparable search frequency levels for the keyword "school bullying." Meanwhile, March, which falls in the middle of the semester, experiences a significant surge in search frequency, as seen in both national data and the top ten states with the highest Asian population.
@@
 
-In summary, by comparing trends in two graphs, our investigation did not reveal any correlation between the Asian population of a state and the frequency of searches related to school bullying.
+### compare top 10 and bottom 10
+
+# Results
+
+# Discussion
+## First discussion point
+
+If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+
+## Correlation between asian population of states and school bullying numbers
+
+As discussed earlier, there has been a significant increase in anti-Asian culture in the United States over the past year.
+Many may be attributed to the spread of misinformation and xenophobic rhetoric related to the COVID-19 pandemic, which has stoked hatred against Asian communities.
+Reports show that 81% of Asian adults state violence against them is increasing.
+(@cit1) Over 3800 hate-related verbal and physical assaults against Asian Americans have been reported during the pandemic.
+(@cit2)
+
+This culture of anti-Asian violence has also impacted schools, with many Asian students reporting incidents of racism and discrimination in the classroom.
+Reports show 68% of attacks were verbal harassment.
+Some students may have faced racially discriminated comments, while others may have experienced exclusion or isolation from their peers.
+These reports have drawn our attention.
+We are eager to learn if there is a need to increase education and awareness among students, as well as efforts to combat racism and discrimination in all forms.
+
+In the previous section, our investigation did not reveal any correlation between the Asian population of a state and the frequency of searches related to school bullying by comparing trends in two graphs.
 While anti-Asian culture is still a large concern in the U.S., it does not seem to have a direct impact on school bullying.
@@
 
-## Weaknesses
+# Weaknesses
 
@@
 
-## Next steps
+# Next steps
 
@@
 
-## Bias
+# Bias
 

### 2023-02-21 Scripts/01-download_data.R

@@ -18,12 +18,12 @@ library(haven)
 #raw_data <- read_dta('/Users/annie/Desktop/Spring 2023/Worlds become data/Analysis on The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying/draft/data/analysis_file.dta')
 
 #### Save data ####
+
 # Locally save the downloaded data in the project space
 Unclean_data <- read.csv(here::here("Inputs/data/raw_data.csv"))
 state_bully_data <- read.csv(here::here("Inputs/data/2021_03_30_monthly_2012_2021_state_bullying_topic.csv"))
 state_cybully_data <- read.csv(here::here("Inputs/data/2021_03_30_monthly_2012_2021_state_cyb_bullying_topic.csv"))
 state_schbully_data <- read.csv(here::here("Inputs/data/2021_03_30_monthly_2012_2021_state_sch_bullying_topic.csv"))
 demographic_data <- read.csv(here::here("Inputs/data/sc-est2019-agesex-civ.csv"))
-#write_csv(raw_data, "inputs/data/raw_data.csv") 
 
          

### 2023-02-21 Outputs/Paper/paper.qmd
added low asian datasets
Slightly changed download data script. Added data cleaning with respect to bottom 10 asian population states. Added to the paper in the top 10 vs bot 10 comparison section, and csv reading

@@
 
+#Reading data for top 10 asian population
 sum_bully_data <- read.csv(here::here("Outputs/data/sum_bully_data.csv"))
@@
 cleaned_schbully_data <- read.csv(here::here("Outputs/data/cleaned_schbully_data.csv"))
+
+#Reading data for bot 10 asian population
+sum_bully_lowasp_data <- read.csv(here::here("Outputs/data/sum_bully_lowasp_data.csv"))
+sum_cybully_lowasp_data <- read.csv(here::here("Outputs/data/sum_cybully_lowasp_data.csv"))
+sum_schbully_lowasp_data <- read.csv(here::here("Outputs/data/sum_schbully_lowasp_data.csv"))
+
+cleaned_bully_lowasp_data <- read.csv(here::here("Outputs/data/cleaned_schbully_lowasp_data.csv"))
+cleaned_cybully_lowasp_data <- read.csv(here::here("Outputs/data/cleaned_schbully_lowasp_data.csv"))
+cleaned_schbully_lowasp_data <- read.csv(here::here("Outputs/data/cleaned_schbully_lowasp_data.csv"))
 
@@
 
-To analysis these data, R programing language (@citeR), tidyverse (@citeTidyverse), and dplyr (@citedplyr) are used.
+To analysis these data, R programming language (@citeR), tidyverse (@citeTidyverse), and dplyr (@citedplyr) are used.
 ggplot2 (@citeggplot2) has been used in order to produce graphic reports.
@@
 
+```{r}
+#| label: lowaspgraph
+#| fig-cap: Bullying searches in the lowest Asian population states.
+#| echo: false
+#| warning: false
+
+sum_bully_lowasp_data |> ggplot(aes(x = date, y = sum)) + 
+  geom_col() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 8)) +
+  labs(
+    title = "All 'Bullying' Searches in Low Asian Population States",
+    x = "Date",
+    y = "Search Frequency",
+    fill = "State Name"
+  )
+
+sum_cybully_lowasp_data |> ggplot(aes(x = date, y = sum)) + 
+  geom_col() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 8)) +
+  labs(
+    title = "'Cyberbullying' Searches in Low Asian Population States",
+    x = "Date",
+    y = "Search Frequency",
+    fill = "State Name"
+  )
+
+sum_schbully_lowasp_data |> ggplot(aes(x = date, y = sum)) + 
+  geom_col() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 8)) +
+  labs(
+    title = "'School Bullying' Searches in Low Asian Population States",
+    x = "Date",
+    y = "Search Frequency",
+    fill = "State Name"
+  )
+```
+
+Figure 6 shows the bullying searches in states with the bottom 10 Asian population.
+In all three metrics, there is a decrease in bullying searches in comparison to bullying searches in the top 10 states.
+The data shows that having a high population of Asian people did have an effect on school bullying searches during the pandemic.
+The higher the Asian population, the more bullying searches there were.
+
+However, one weakness of this comparison is that there is sampling bias with this set.
+The total population numbers for the bottom 10 Asian population states are dwarfed by the total population numbers of the top 10 Asian population states.
+So naturally, there would be less bullying searches in a state like Montana, which has around 2.7% of California's total population.
+This is where our approach of using raw search data reaches it's limit, as we cannot draw an accurate comparison of search ratios due to the massive difference in total population numbers.
+
 # Results

### 2023-02-21 Scripts/01-download_data.R

@@ -21,9 +21,9 @@ library(haven)
 
 # Locally save the downloaded data in the project space
 Unclean_data <- read.csv(here::here("Inputs/data/raw_data.csv"))
-state_bully_data <- read.csv(here::here("Inputs/data/2021_03_30_monthly_2012_2021_state_bullying_topic.csv"))
-state_cybully_data <- read.csv(here::here("Inputs/data/2021_03_30_monthly_2012_2021_state_cyb_bullying_topic.csv"))
-state_schbully_data <- read.csv(here::here("Inputs/data/2021_03_30_monthly_2012_2021_state_sch_bullying_topic.csv"))
+state_bully_data_raw <- read.csv(here::here("Inputs/data/2021_03_30_monthly_2012_2021_state_bullying_topic.csv"))
+state_cybully_data_raw <- read.csv(here::here("Inputs/data/2021_03_30_monthly_2012_2021_state_cyb_bullying_topic.csv"))
+state_schbully_data_raw <- read.csv(here::here("Inputs/data/2021_03_30_monthly_2012_2021_state_sch_bullying_topic.csv"))
 demographic_data <- read.csv(here::here("Inputs/data/sc-est2019-agesex-civ.csv"))
 
          

### 2023-02-21 Outputs/Paper/paper.qmd
Update paper.qmd

--- 2023-02-21 Outputs/Paper/paper.qmd
@@
 
-sum_bully_data |> ggplot(aes(x = date, y = sum)) + 
+cleaned_bully_data |> ggplot(aes(x = date, 
+                                    y = hits,
+                                    fill = State.Name)) + 
   geom_col() +
@@
 
-sum_cybully_data |> ggplot(aes(x = date, y = sum)) + 
+cleaned_cybully_data |> ggplot(aes(x = date, 
+                                    y = hits,
+                                    fill = State.Name)) + 
   geom_col() +
@@
 
-sum_schbully_data |> ggplot(aes(x = date, y = sum)) + 
+cleaned_schbully_data |> ggplot(aes(x = date, 
+                                    y = hits,
+                                    fill = State.Name)) + 
   geom_col() +
@@
 ```
+
+Figure 1 shows the number of Google hits for all 'bullying' searches in the top ten states with the highest Asian populations.
+According to Bacher-Hicks, there is a positive correlation between search intensity and frequency of victimization (Bacher-Hicks, 8).
+While unusually high peaks occur during March 2017 and 2018 with the frequency reaching 400, and the lowest clicks during summer months with numbers consistently below 200, the overall trend from 2016 to the start of the pandemic shows an overall decline.
+In 2020, when the pandemic began well known to the public, there continues to be a decline in overall search intensity.
+On average the 2020 frequency was lower than in previous years.
+This was the same time period when most schools were shut down and classes were offered online which could lead to the conclusion that bullying decreased when students were not attending classes in person.
+There is a slight rise in the summer of 2020 that is compared to the 2016 data and a reverse of the declining trends seen over the years, however, the following summer this number is reduced to the lowest number seen over the years.
+This blimp at the start of the pandemic could be a result of students being in lock down with more online time.
+Overall, the trend in search frequency and therefore, victimization, has been relatively stable with a slight decline up to the start of the pandemic and then we see further declines as a result of online learning, school closures and isolation during COVID-19.
+This graph shows there was no increase in bullying of Asian students by their peers during the pandemic in the top ten states with high Asian populations.
 
@@
 ## Correlation between asian population of states and school bullying numbers
+
+Anti-Asian violence skyrocketed over the pandemic.
+The Center for the Study of Hate and Extremism published a report showing how anti-Asian hate crimes grew by 339 percent last year compared to the year before.
+The racism was fueled by the pandemic, mainly occurring in highly populated urban cities like New York, San Francisco, and Los Angeles.
+The percentages of Asian hate crimes in New York rose from 30 to 133 and in San Francisco from 9 to 60.
+American culture pretends Asian Americans face no discrimination or racism.
+There are countless examples where when the U.S.
+was faced with an economic downturn, Asian Americans were affected.
+The 1982 killing of Vincent Chin in Detroit came after the 1980-1982 Detroit recession and The Page Act of 1875, America's first immigration law that banned Chinese women after the Great Panic of 1873.
+It's safe to assume an economic horror like the pandemic would lead to hate.
+It was disconcerting reading about the different hate acts that occurred, and it was clear there needed to be culturally appropriate and accessible community safety programs.
+From the data provided, we decided to clean it, focusing on the states with an Asian population.
+There has been mainstream media coverage of anti-Asian racism but little effort toward the Asian American Youth.
+(could be apart of introduction)
 
@@
 
-\newpage
+Google's reported data doesn't consider the sample of users or data points.
+There is an evident sample bias that takes occurs in this study.
+The general population can be under or overrepresented.
+It's unsure which students' searches are being used, making their age and ethnicity unclear.
+The broad population must be represented and used in our data.
+User behavior is measured by how many hits particular buzzword use.
+This measurement can be flawed as students may search other buzzwords or not use the internet to gather research on bullying and how to receive help.
+Google may only report positive trends and ignore negative ones leaving the data skewed.
+
+People have the fundamental right to privacy in all aspects of life.
+When on the internet, the average individual is dealing with information about their personal life, health, and sensitive topics they may not want to be shared.
+When choosing what data to report on, Google must be aware of this and careful that they're not impinging on the fundamental human right of privacy.
+There needs to be more information out there to educate the public on how their information is being used.
+The average citizen must be aware that their data is collected and used for reports.
+Hackers are constantly trying to infiltrate and use users' information for their gain.
+Security measures need to be introduced to protect search data from unauthorized access.
+The results an individual gets based on their search relate to their demographic and algorithm.
+Our dataset needs to be looked at with this in mind.
+An ethical lens must always be used when looking at people's search data to prevent discriminatory practices.
 

### 2023-02-21 Outputs/Paper/paper.qmd

--- 2023-02-21 Outputs/Paper/paper.qmd
@@
 
+Figure 1 shows the number of Google hits for all 'bullying' searches in the top ten states with the highest Asian populations.
+According to Bacher-Hicks, there is a positive correlation between search intensity and frequency of victimization (Bacher-Hicks, 8).
+While unusually high peaks occur during March 2017 and 2018 with the frequency reaching 400, and the lowest clicks during summer months with numbers consistently below 200, the overall trend from 2016 to the start of the pandemic shows an overall decline.
+In 2020, when the pandemic began well known to the public, there continues to be a decline in overall search intensity.
+On average the 2020 frequency was lower than in previous years.
+This was the same time period when most schools were shut down and classes were offered online which could lead to the conclusion that bullying decreased when students were not attending classes in person.
+There is a slight rise in the summer of 2020 that is compared to the 2016 data and a reverse of the declining trends seen over the years, however, the following summer this number is reduced to the lowest number seen over the years.
+This blimp at the start of the pandemic could be a result of students being in lock down with more online time.
+Overall, the trend in search frequency and therefore, victimization, has been relatively stable with a slight decline up to the start of the pandemic and then we see further declines as a result of online learning, school closures and isolation during COVID-19.
+This graph shows there was no increase in bullying of Asian students by their peers during the pandemic in the top ten states with high Asian populations.
+
 # Data
@@
 
+If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+
+## Correlation between asian population of states and school bullying numbers
+
+Anti-Asian violence skyrocketed over the pandemic.
+The Center for the Study of Hate and Extremism published a report showing how anti-Asian hate crimes grew by 339 percent last year compared to the year before.
+The racism was fueled by the pandemic, mainly occurring in highly populated urban cities like New York, San Francisco, and Los Angeles.
+The percentages of Asian hate crimes in New York rose from 30 to 133 and in San Francisco from 9 to 60.
+American culture pretends Asian Americans face no discrimination or racism.
+There are countless examples where when the U.S.
+was faced with an economic downturn, Asian Americans were affected.
+The 1982 killing of Vincent Chin in Detroit came after the 1980-1982 Detroit recession and The Page Act of 1875, America's first immigration law that banned Chinese women after the Great Panic of 1873.
+It's safe to assume an economic horror like the pandemic would lead to hate.
+It was disconcerting reading about the different hate acts that occurred, and it was clear there needed to be culturally appropriate and accessible community safety programs.
+From the data provided, we decided to clean it, focusing on the states with an Asian population.
+There has been mainstream media coverage of anti-Asian racism but little effort toward the Asian American Youth.
+(could be apart of introduction)
+
+As discussed earlier, there has been a significant increase in anti-Asian culture in the United States over the past year.
+Many may be attributed to the spread of misinformation and xenophobic rhetoric related to the COVID-19 pandemic, which has stoked hatred against Asian communities.
+Reports show that 81% of Asian adults state violence against them is increasing.
+Over 3800 hate-related verbal and physical assaults against Asian Americans have been reported during the pandemic.
+
+This culture of anti-Asian violence has also impacted schools, with many Asian students reporting incidents of racism and discrimination in the classroom.
+Reports show 68% of attacks were verbal harassment.
+Some students may have faced racially discriminated comments, while others may have experienced exclusion or isolation from their peers.
+These reports have drawn our attention.
+We are eager to learn if there is a need to increase education and awareness among students, as well as efforts to combat racism and discrimination in all forms.
+
 We conducted a study to determine if there was a correlation between the increasing anti-Asian sentiment and school bullying in the United States.
 To do this, we analyzed the correlation between the search frequency for the term "school bullying" and the Asian population of each state.
-Figures 4 and 5 were used to compare the search frequency of the keyword "school bullying" and the date.
+Figures 2 and 3 were used to compare the search frequency of the keyword "school bullying" and the date.
 

### 2023-02-21 Outputs/Paper/paper.qmd
update paper 4

@@
 
-You can and should cross-reference sections and sub-sections. For instance, @sec-data and @sec-first-point.
-
-talking points 1) why asian population? because anti-asian violence in the usa grew. we want to see if anti-asian violence was also reflected in school and cyber bullying (introduction). (will)
-
-2)  our replicated graphs show that bullying numbers dropped during covid, (wil)
-
-3)  But there wasnt a significant correlation between asian population of states and school bullying numbers (annie)
-
-4)  do a comparison of top 10 asian vs bottom 10 asian population states to see if asian population actually matters in school bullying (jason)
-
-5)  lack of correlation testing, this is only reported bullying, not reflected of everyone getting bullied. only those that search (annie)
-
-6)  next steps: try asian population in certain schools instead of states? a hard comparison between asian bullying and violence? (annie)
-
-7)  bias of only reported data (sampling) with people that only searches for bullying.
-ethics of using peoples search data.
-unreliability of measurement.
-not every1 uses google for searches or bullying help.
-google's algorithm will shift towards anti-bullying stuff for people that search for it.
-(will)
+Anti-Asian violence skyrocketed over the pandemic.
+The Center for the Study of Hate and Extremism published a report showing how anti-Asian hate crimes grew by 339 percent last year compared to the year before.
+The racism was fueled by the pandemic, mainly occurring in highly populated urban cities like New York, San Francisco, and Los Angeles.
+The percentages of Asian hate crimes in New York rose from 30 to 133 and in San Francisco from 9 to 60.
+American culture pretends Asian Americans face no discrimination or racism.
+There are countless examples where when the U.S.
+was faced with an economic downturn, Asian Americans were affected.
+The 1982 killing of Vincent Chin in Detroit came after the 1980-1982 Detroit recession and The Page Act of 1875, America's first immigration law that banned Chinese women after the Great Panic of 1873.
+It's safe to assume an economic horror like the pandemic would lead to hate.
+It was disconcerting reading about the different hate acts that occurred, and it was clear there needed to be culturally appropriate and accessible community safety programs.
+From the data provided, we decided to clean it, focusing on the states with an Asian population.
+There has been mainstream media coverage of anti-Asian racism but little effort toward the Asian American Youth.
 
@@
 
+# Data
+
+## Data collection
+
+The data used in this study were pulled from reproducible package of article "Data and code for: The COVID-19 pandemic disrupted both school bullying and cyberbullying." (@cit4) According to the article, raw data were provided from Google Trends and Youth Risk Behavior Survey.
+
+To analysis these data, R programming language (@citeR), tidyverse (@citeTidyverse), and dplyr (@citedplyr) are used.
+ggplot2 (@citeggplot2) has been used in order to produce graphic reports.
+The use of knitr (@citeknitr) helped us to generate tables.
+Lubridate (@citelubridate) are used to reformat dates.
+
+## Measurements
+All the data we used is from after 2016.
+In our study, bullying data includes school bullying data and cyberbullying data.
+We measure the intensity of bullying by number of hits in one day.
+In the paper, we will refer it as search frequency.
+
+## Data Analysis
+
+### Bullying search droped after COVID-19
+
 ```{r}
-#| label: bullydata
-#| fig-cap: 3 graphs lol
+#| label: All Bullying Searches in High Asian Population States
+#| fig-cap: All Bullying Searches in High Asian Population States
 #| echo: false
@@
   )
+```
 
+```{r}
+#| label: Cyberbullying Searches in High Asian Population States
+#| fig-cap: Cyberbullying Searches in High Asian Population States
+#| echo: false
+#| warning: false
+library(tidyverse)
 sum_cybully_data |> ggplot(aes(x = date, y = sum)) + 
@@
   )
+```
 
+```{r}
+#| label: School Bullying Searches in High Asian Population States
+#| fig-cap: School Bullying Searches in High Asian Population States
+#| echo: false
+#| warning: false
+library(tidyverse)
 sum_schbully_data |> ggplot(aes(x = date, y = sum)) + 
@@
 
-# Data
-
-## Data collection
-
-The data used in this study were pulled from reproducible package of article "Data and code for: The COVID-19 pandemic disrupted both school bullying and cyberbullying." (@cit4) According to the article, raw data were provided from Google Trends and Youth Risk Behavior Survey.
-
-To analysis these data, R programming language (@citeR), tidyverse (@citeTidyverse), and dplyr (@citedplyr) are used.
-ggplot2 (@citeggplot2) has been used in order to produce graphic reports.
-The use of knitr (@citeknitr) helped us to generate tables.
-Lubridate (@citelubridate) are used to reformat dates.
-
-## Measurements
-All the data we used is from after 2016.
-In our study, bullying data includes school bullying data and cyberbullying data.
-We measure the intensity of bullying by number of hits in one day.
-In the paper, we will refer it as search frequency.
-
-## Data Analysis
-
-### bullying number droped after covid
-
 ### Correlation between asian population of states and school bullying numbers
-
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
-
-## Correlation between asian population of states and school bullying numbers
-
-Anti-Asian violence skyrocketed over the pandemic.
-The Center for the Study of Hate and Extremism published a report showing how anti-Asian hate crimes grew by 339 percent last year compared to the year before.
-The racism was fueled by the pandemic, mainly occurring in highly populated urban cities like New York, San Francisco, and Los Angeles.
-The percentages of Asian hate crimes in New York rose from 30 to 133 and in San Francisco from 9 to 60.
-American culture pretends Asian Americans face no discrimination or racism.
-There are countless examples where when the U.S.
-was faced with an economic downturn, Asian Americans were affected.
-The 1982 killing of Vincent Chin in Detroit came after the 1980-1982 Detroit recession and The Page Act of 1875, America's first immigration law that banned Chinese women after the Great Panic of 1873.
-It's safe to assume an economic horror like the pandemic would lead to hate.
-It was disconcerting reading about the different hate acts that occurred, and it was clear there needed to be culturally appropriate and accessible community safety programs.
-From the data provided, we decided to clean it, focusing on the states with an Asian population.
-There has been mainstream media coverage of anti-Asian racism but little effort toward the Asian American Youth.
-(could be apart of introduction)
 
@@
 
-### compare top 10 and bottom 10
+### Comparing top 10 with highest Asian population and bottom 10 states with lowest Asian population
 
@@
 # Discussion
-## First discussion point
+## Bullying search relate to COVID-19
 
@@
 
-## Third discussion point
+## Comparing top 10 with highest Asian population and bottom 10 states with lowest Asian population
 
@@
 
+\newpage
+
 # References

### 2023-02-21 Outputs/Paper/paper.qmd
update paper 5

@@
 In the study, our estimated population vary for different datasets.
-The population of the data used in figures 1, 2, 3, and 4 contains people who live in the top ten states with the highest Asian population.
+The population of the data used in figures 1, 2, and 3 contains people who live in the top ten states with the highest Asian population.
 These states includes California, Florida, Hawaii, Illinois, Massachusetts, New Jersey, New York, Texas, Virginia, and Washington.
-(@cit3) Nationwide data includes population of all people who live in the United States.
+(@cit3) The population of data used in figures 5, 6, and 7 are people who live in the bottom ten states with the lowest Asian population.
+These states includes Arkansas, Maine, Mississippi, Montana, North Dakota, South Dakota, Alabama, West Virginia, Wyoming, and Kentucky.Nationwide data used in figure 4 includes population of all people who live in the United States.
 
@@
 
-```{r}
-#| label: School Bullying Searches in High Asian Population States
-#| fig-cap: School Bullying Searches in High Asian Population States
-#| echo: false
-#| warning: false
-library(tidyverse)
-sum_schbully_data |> ggplot(aes(x = date, y = sum)) + 
-  geom_col() +
-  theme(axis.text.x = element_text(angle = 45,hjust=1), 
-        axis.line = element_line(colour = "black"),
-        title = element_text(size = 8)) +
-  labs(
-    title = "'School Bullying' Searches in High Asian Population States",
-    x = "Date",
-    y = "Search Frequency",
-    fill = "State Name"
-  )
-
-```
-
 Figure 1 shows the number of Google hits for all 'bullying' searches in the top ten states with the highest Asian populations.
@@
 To do this, we analyzed the correlation between the search frequency for the term "school bullying" and the Asian population of each state.
-Figures 2 and 3 were used to compare the search frequency of the keyword "school bullying" and the date.
+Figures 3 and 4 were used to compare the search frequency of the keyword "school bullying" and the date.
 
@@
 
-Figure 4  shows the frequency of the keyword "school bullying" searched online within the top ten states with the highest Asian population.
+Figure 3  shows the frequency of the keyword "school bullying" searched online within the top ten states with the highest Asian population.
 The graph indicates that March 1st, 2018, had the highest number of searches for "school bullying" at over 400.
@@
 
-Figure 5 presents data on the search frequency of the keyword "school bullying" nationally since 2016.
+Figure 4 presents data on the search frequency of the keyword "school bullying" nationally since 2016.
 Like Figure 4, March 1st, 2018, had the highest search frequency at 2000 nationally.
@@
 
-Upon comparing Figure 4 and Figure 5, we observed a consistent trend.
+Upon comparing Figure 3 and Figure 4, we observed a consistent trend.
 Notably, the months of January and September, which mark the beginning of school, exhibit comparable search frequency levels for the keyword "school bullying." Meanwhile, March, which falls in the middle of the semester, experiences a significant surge in search frequency, as seen in both national data and the top ten states with the highest Asian population.

### 2023-02-21 Outputs/Paper/paper.qmd
update results

@@
 # Results
+According to our previous investigations, search frequency for bullying in the top ten states with the highest Asian population slightly decreased after the start of the pandemic.
+This trend not only affected overall bullying search, but also had an impact on the search frequency trend for cyberbullying.
+Our observations indicate that the pandemic did not increase bullying in Asian American students.
+A later study that examined the correlation between the Asian population of states and school bullying numbers showed similar results.
+The study compared search intensity trends for the keyword "school bullying" in the top 10 states with the highest Asian population to nationwide data, but found no correlation between school bullying searches and the Asian population of the state.
+Further evaluation compared data from the top 10 states with the highest Asian population to the bottom 10 states with the lowest Asian population.
+This research showed that having a high population of Asian people did have an effect on school bullying searches during the pandemic, with higher Asian populations resulting in more bullying searches.
+Our study took three different angles to observe the relationship between the Asian population and search frequency in bullying, but only one of them showed a correlation.
+Therefore, future studies are needed to determine if a statistically significant correlation exists between the Asian population and bullying.
+It's important to continue investigating and addressing the issue of bullying in all populations and to develop effective interventions and prevention strategies to reduce its occurrence.
 

### 2023-02-21 Scripts/05-testing_graphs.R
delete testing graph

@@ -1,38 +1,0 @@
-state_bully_data |> ggplot(aes(x = date, y = hits, color = State.Name)) + geom_point() + theme(axis.text.x = element_text(angle = 45,hjust=1))
-bully_dates_test <- state_bully_data %>% mutate(year = lubridate::year(date), 
-                      month = lubridate::month(date), 
-                      day = lubridate::day(date))
-bully_dates_test <- bully_dates_test |> filter(month == 1 | month == 7)
-bully_dates_test <- bully_dates_test |> filter(year > 2015)
-
-bully_dates_test_2 <- bully_dates_test|>group_by(date)|>summarise(sum = sum(hits))
-
-bully_dates_test |> ggplot(aes(x = date, y = hits)) + 
-  geom_point(size = 3, alpha = 0.5) + 
-  geom_line() + 
-  theme(axis.text.x = element_text(angle = 45,hjust=1))
-
-bully_dates_test_2 |> ggplot(aes(x = date, y = sum)) + 
-  geom_col() + 
-  theme(axis.text.x = element_text(angle = 45,hjust=1))
-
-state_bully_data_2 <- state_bully_data_2 |> filter(dma_json_code == 'US-CA' | dma_json_code == 'US-NY' | dma_json_code == 'US-TX' |
-                                                 dma_json_code == 'US-NJ' | dma_json_code == 'US-WA' | dma_json_code == 'US-IL' |
-                                                 dma_json_code == 'US-HI' | dma_json_code == 'US-FL' | dma_json_code == 'US-VA' |
-                                                 dma_json_code == 'US-MA', na.rm = TRUE)
-
-state_bully_data_2 <- state_bully_data_2 |> mutate(year = lubridate::year(date), 
-                                                month = lubridate::month(date), 
-                                                day = lubridate::day(date))
-
-state_bully_data_2 <- state_bully_data_2 |> filter(month == 1 | month == 7 | month == 9 | month == 3)
-state_bully_data_2 <- state_bully_data_2 |> filter(year > 2015)
-state_bully_data_2 <- state_bully_data_2|>group_by(date)|>summarise(sum = sum(hits))
-
-state_bully_data |> ggplot(aes(x = date, y = sum)) + 
-  geom_col() +
-  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
-  labs(
-    x = "School Year Date Intervals",
-    y = "Sum of Searches by Investigated States"
-  )

### 2023-02-21 Outputs/Paper/paper.qmd
cross reference

@@
 In the study, our estimated population vary for different datasets.
-The population of the data used in figures 1, 2, and 3 contains people who live in the top ten states with the highest Asian population.
+The population of the data used in @fig-1, @fig-2, and @fig-3 contains people who live in the top ten states with the highest Asian population.
 These states includes California, Florida, Hawaii, Illinois, Massachusetts, New Jersey, New York, Texas, Virginia, and Washington.
-(@cit3) The population of data used in figures 5, 6, and 7 are people who live in the bottom ten states with the lowest Asian population.
-These states includes Arkansas, Maine, Mississippi, Montana, North Dakota, South Dakota, Alabama, West Virginia, Wyoming, and Kentucky.Nationwide data used in figure 4 includes population of all people who live in the United States.
+(@cit3) The population of data used in @fig-5, @fig-6, and @fig-7 are people who live in the bottom ten states with the lowest Asian population.
+These states includes Arkansas, Maine, Mississippi, Montana, North Dakota, South Dakota, Alabama, West Virginia, Wyoming, and Kentucky.Nationwide data used in @fig-4 includes population of all people who live in the United States.
 
@@
 ```{r}
-#| label: All Bullying Searches in High Asian Population States
+#| label: fig-1
 #| fig-cap: All Bullying Searches in High Asian Population States
@@
 ```{r}
-#| label: Cyberbullying Searches in High Asian Population States
+#| label: fig-2
 #| fig-cap: Cyberbullying Searches in High Asian Population States
@@
 
-Figure 1 shows the number of Google hits for all 'bullying' searches in the top ten states with the highest Asian populations.
+@fig-1 shows the number of Google hits for all 'bullying' searches in the top ten states with the highest Asian populations.
 According to Bacher-Hicks, there is a positive correlation between search intensity and frequency of victimization (Bacher-Hicks, 8).
@@
 To do this, we analyzed the correlation between the search frequency for the term "school bullying" and the Asian population of each state.
-Figures 3 and 4 were used to compare the search frequency of the keyword "school bullying" and the date.
+@fig-3 and @fig-4 were used to compare the search frequency of the keyword "school bullying" and the date.
 
 ```{r}
-#| label: School bullying searches in top 10 states with highest asian population
+#| label: fig-3
 #| fig-cap: "School bullying searches in top 10 states with highest asian population"
@@
 
-Figure 3  shows the frequency of the keyword "school bullying" searched online within the top ten states with the highest Asian population.
+@fig-3 shows the frequency of the keyword "school bullying" searched online within the top ten states with the highest Asian population.
 The graph indicates that March 1st, 2018, had the highest number of searches for "school bullying" at over 400.
@@
 
-```{r figure2}
-#| label: School bullying searches nationwide
+```{r}
+#| label: fig-4
 #| fig-cap: School bullying searches nationwide
@@
 
-Figure 4 presents data on the search frequency of the keyword "school bullying" nationally since 2016.
-Like Figure 4, March 1st, 2018, had the highest search frequency at 2000 nationally.
+@fig-4 presents data on the search frequency of the keyword "school bullying" nationally since 2016.
+Like @fig-4, March 1st, 2018, had the highest search frequency at 2000 nationally.
 On the other hand, July's search frequency was always at the lowest level, with data from 2016 to 2021 never exceeding 750.
@@
 
-Upon comparing Figure 3 and Figure 4, we observed a consistent trend.
+Upon comparing @fig-3 and @fig-4, we observed a consistent trend.
 Notably, the months of January and September, which mark the beginning of school, exhibit comparable search frequency levels for the keyword "school bullying." Meanwhile, March, which falls in the middle of the semester, experiences a significant surge in search frequency, as seen in both national data and the top ten states with the highest Asian population.
@@
 ```{r}
-#| label: lowaspgraph
+#| label: fig-5
 #| fig-cap: Bullying searches in the lowest Asian population states.
@@
   )
+```
 
+```{r}
+#| label: fig-6
+#| fig-cap: Cyberbullying searches in the lowest Asian population states.
+#| echo: false
+#| warning: false
 sum_cybully_lowasp_data |> ggplot(aes(x = date, y = sum)) + 
@@
   )
+```
 
+```{r}
+#| label: fig-7
+#| fig-cap: School bullying searches in the lowest Asian population states.
+#| echo: false
+#| warning: false
 sum_schbully_lowasp_data |> ggplot(aes(x = date, y = sum)) + 
@@
 
-Figure 6 shows the bullying searches in states with the bottom 10 Asian population.
+@fig-5 shows the bullying searches in states with the bottom 10 Asian population.
 In all three metrics, there is a decrease in bullying searches in comparison to bullying searches in the top 10 states.

### 2023-02-21 Outputs/Paper/paper.qmd
update paper

@@
 ### Correlation between asian population of states and school bullying numbers
-
-As discussed earlier, there has been a significant increase in anti-Asian culture in the United States over the past year.
-Many may be attributed to the spread of misinformation and xenophobic rhetoric related to the COVID-19 pandemic, which has stoked hatred against Asian communities.
-Reports show that 81% of Asian adults state violence against them is increasing.
-Over 3800 hate-related verbal and physical assaults against Asian Americans have been reported during the pandemic.
-
-This culture of anti-Asian violence has also impacted schools, with many Asian students reporting incidents of racism and discrimination in the classroom.
-Reports show 68% of attacks were verbal harassment.
-Some students may have faced racially discriminated comments, while others may have experienced exclusion or isolation from their peers.
-These reports have drawn our attention.
-We are eager to learn if there is a need to increase education and awareness among students, as well as efforts to combat racism and discrimination in all forms.
 
@@
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+write a little here
 
@@
 ## Comparing top 10 with highest Asian population and bottom 10 states with lowest Asian population
+write a little here
 

### 2023-02-21 Outputs/Paper/paper.qmd
Update paper.qmd

@@
 This blimp at the start of the pandemic could be a result of students being in lock down with more online time.
+
+@fig-2 shows the frequency of the amount of searches for "Cyberbullying".
+The naked eye test will tell you that the amount of cyberbullying searches have slightly decreased every year from 2016.
+The lowest points of the graph occur from 2020 onwards.
+The summer months are always the lowest througout the five years with a slight decrease every year.
+The peak of the data happens in March of 2016 climbing up to 500 compared to March 2020 when it's 250.
+This is a drast difference between pre and post pandemic.
+
 Overall, the trend in search frequency and therefore, victimization, has been relatively stable with a slight decline up to the start of the pandemic and then we see further declines as a result of online learning, school closures and isolation during COVID-19.

### 2023-02-21 Outputs/Paper/paper.qmd
update title

--- 2023-02-21 Outputs/Paper/paper.qmd
@@
 ---
-title: "Analysis on The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying"
-subtitle: "My subtitle if needed"
+title: "The COVID-19 Pandemic impact on bullying search intensity relate with Asian population"
 author: 

### 2023-02-21 Outputs/Paper/paper.qmd

@@
 ---
-title: "The COVID-19 Pandemic impact on bullying search intensity relate with Asian population"
+title: "The COVID-19 Pandemic's Impact on Bullying Search Intensity with respect to Asian Population"
 author: 

### 2023-02-21 Outputs/Paper/paper.qmd
update paper

--- 2023-02-21 Outputs/Paper/paper.qmd
@@
   - Annie Yan
-thanks: "Code and data are available at: https://github.com/AnnieYan0807/Analysis-on-The-COVID-19-Pandemic-Disrupted-Both-School-Bullying-and-Cyberbullying."
+thanks: "Code and data are available at: https://github.com/AnnieYan0807/Analysis-on-The-COVID-19-Pandemic-Disrupted-Both-School-Bullying-and-Cyberbullying.
+The replication on the SSRP can be found at : https://doi.org/10.48152/ssrp-54f4-p919"
 date: "`r Sys.time()`"

### 2023-02-21 Outputs/Paper/starter folder draft.R

@@ -1,23 +1,0 @@
-###draft
-
-Our data is of penguins (@fig-bills).
-
-Talk more about it.
-
-Also bills and their average (@fig-billssssss). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work.)
-
-
-Talk way more about it. 
-
-
-# Model
-
-$$
-  Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}
-  $$ {#eq-bayes}
-    
-    @eq-bayes seems useful, eh?
-      
-      Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful. 
-
-We can use maths by including latex between dollar signs, for instance $\theta$.

### 2023-02-21 Outputs/Paper/paper.qmd
Added section in quarto

@@
 
-### Bullying search droped after COVID-19
+### Bullying search dropped after COVID-19
 
@@
 
-### Comparing top 10 with highest Asian population and bottom 10 states with lowest Asian population
+### Comparing the Top 10 Asian Population states with the Bottom 10
 
@@
 
-@fig-5 shows the bullying searches in states with the bottom 10 Asian population.
+\newpage
+
+@fig-5, @fig-6, and @fig-7 shows the bullying searches in states with the 10 lowest percentage of Asian population.
 In all three metrics, there is a decrease in bullying searches in comparison to bullying searches in the top 10 states.
@@
 The higher the Asian population, the more bullying searches there were.
-
-However, one weakness of this comparison is that there is sampling bias with this set.
-The total population numbers for the bottom 10 Asian population states are dwarfed by the total population numbers of the top 10 Asian population states.
-So naturally, there would be less bullying searches in a state like Montana, which has around 2.7% of California's total population.
-This is where our approach of using raw search data reaches it's limit, as we cannot draw an accurate comparison of search ratios due to the massive difference in total population numbers.
 
@@
 # Discussion
-## Bullying search relate to COVID-19
-
-write a little here
 
@@
 
-## Comparing top 10 with highest Asian population and bottom 10 states with lowest Asian population
-write a little here
+## Comparing the Top 10 Asian Population states with the Bottom 10
+The top 10 Asian population states experienced more school and cyber bullying than the bottom 10 Asian population states.
+From (@cit7), there has been a 70% increase in Asian American cyberbullying in 2020.
+Anti-Asian xenophobia fueled by Covid-19 has led to an increase of hate towards Asian-Americans.
+With this in mind, Asian population does make an effect with respect to the disparity between bullying searches from the top 10 Asian population states with bullying searches from the bottom 10 Asian population states.
 
@@
 
+In @fig-5, @fig-6, and @fig-7, there is sampling bias with these datasets.
+The total population numbers for the bottom 10 Asian population states are dwarfed by the total population numbers of the top 10 Asian population states.
+So naturally, there would be less bullying searches in a state like Montana, which has around 2.7% of California's total population.
+This is where our approach of using raw search data reaches it's limit, as we cannot draw an accurate comparison of search ratios due to the massive difference in total population numbers.
+
 \newpage

### 2023-02-22 Outputs/Paper/paper.qmd
Update paper.qmd

@@
 date-format: "D MMMM YYYY"
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "The Covid-19 pandemic incited a wave of anti-Asian hate crimes across the United States including derogatory language in the media, random bullying, and violent, senseless murders.
+This paper analyzes how high school closures and the shift to online learning by schools throughout the pandemic, impacted incidents of bullying of Asian students compared to non Asian students when compared to pre-pandemic trends and in-person learning.
+Results suggest that while the overall trend in bullying of high school students has been in decline across all states between 2016-2021, with a larger drop during Covid-19, the states with high Asian populations saw greater incidents of bullying when compared to states with low Asian populations over the six year period.
+These findings tell both a good news story of declining bullying trends in the US school system and a highly concerning narrative that anti-Asian bullying is not a result of Covid-19, but rather an intensified awareness of pre-existing systemic racism in our learning institutions."
 format: pdf

### 2023-02-22 Outputs/Paper/paper.qmd
edit abstract

--- 2023-02-21 Outputs/Paper/paper.qmd
@@
 date-format: "D MMMM YYYY"
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "The Covid-19 pandemic incited a wave of anti-Asian hate crimes across the United States.
+This paper analyzes how school closures and the shift to online learning impacted searches about bullying in states with high and low Asian population with a comparison to pre-pandemic dates and with in-person learning.
+Results suggest that while the overall trend in bullying of high school students has been in decline nationwide between 2016-2021, with a larger drop during Covid-19, the states with high percentages of Asian populations saw a higher intensity of bullying searches when compared to states with low percentages of Asian populations over the six year period.
+These findings tell two stores: One of declining bullying trends in the US school system and one showing that anti-Asian bullying is not a result of Covid-19, but rather a sympton of a pre-existing systemic racism in our learning institutions."
 format: pdf
@@
 Anti-Asian violence skyrocketed over the pandemic.
-The Center for the Study of Hate and Extremism published a report showing how anti-Asian hate crimes grew by 339 percent last year compared to the year before.
-The racism was fueled by the pandemic, mainly occurring in highly populated urban cities like New York, San Francisco, and Los Angeles.
+The Center for the Study of Hate and Extremism published a report showing how anti-Asian hate crimes grew by 339% last year compared to the year before.
+These hate crimes were fueled by the pandemic, mainly occurring in highly populated urban cities like New York, San Francisco, and Los Angeles.
 The percentages of Asian hate crimes in New York rose from 30 to 133 and in San Francisco from 9 to 60.
-American culture pretends Asian Americans face no discrimination or racism.
-There are countless examples where when the U.S.
+American culture pretends Asian-Americans face no discrimination or racism.
+There were countless examples where when the U.S.
 was faced with an economic downturn, Asian Americans were affected.

### 2023-02-22 Outputs/Paper/paper.qmd
Update paper.qmd

--- 2023-02-22 Outputs/Paper/paper.qmd
@@
 Results suggest that while the overall trend in bullying of high school students has been in decline across all states between 2016-2021, with a larger drop during Covid-19, the states with high Asian populations saw greater incidents of bullying when compared to states with low Asian populations over the six year period.
-These findings tell both a good news story of declining bullying trends in the US school system and a highly concerning narrative that anti-Asian bullying is not a result of Covid-19, but rather an intensified awareness of pre-existing systemic racism in our learning institutions."
+These findings tell both a good news story of declining bullying trends in the US school system and a highly concerning narrative that anti-Asian bullying is not a result of Covid-19, but rather an intensified awareness of pre-existing racism.
 format: pdf
@@
 
-Anti-Asian violence skyrocketed over the pandemic.
-The Center for the Study of Hate and Extremism published a report showing how anti-Asian hate crimes grew by 339 percent last year compared to the year before.
-The racism was fueled by the pandemic, mainly occurring in highly populated urban cities like New York, San Francisco, and Los Angeles.
-The percentages of Asian hate crimes in New York rose from 30 to 133 and in San Francisco from 9 to 60.
+Anti-Asian violence skyrocketed during the Covid-19 pandemic.
+The Center for the Study of Hate and Extremism published a report showing how anti-Asian hate crimes in the United States grew by 339% from 2020 to 2021 - the height of the global crisis.
+This increase in racism, fueled by the pandemic, occurred mainly in highly populated urban cities where the population of people of Asian descent are more predominant.
+For example, the percentages of Asian hate crimes in New York rose from 30% to 133% and in San Francisco from 9% to 60%.
 American culture pretends Asian Americans face no discrimination or racism.

### 2023-02-22 Outputs/Paper/paper.qmd
Grammar check, spell check and reformatting quarto doc

--- 2023-02-22 Outputs/Paper/paper.qmd
@@
 ## Estimand
-In the study, our estimated population vary for different datasets.
-The population of the data used in @fig-1, @fig-2, and @fig-3 contains people who live in the top ten states with the highest Asian population.
-These states includes California, Florida, Hawaii, Illinois, Massachusetts, New Jersey, New York, Texas, Virginia, and Washington.
-(@cit3) The population of data used in @fig-5, @fig-6, and @fig-7 are people who live in the bottom ten states with the lowest Asian population.
-These states includes Arkansas, Maine, Mississippi, Montana, North Dakota, South Dakota, Alabama, West Virginia, Wyoming, and Kentucky.Nationwide data used in @fig-4 includes population of all people who live in the United States.
+
+In our study, our estimated population varies between different datasets.
+The population depicted in @fig-1, @fig-2, and @fig-3 contains people that searched up bullying online that live in the states with the top 10 highest percentages of Asian population.
+These states are: California, Florida, Hawaii, Illinois, Massachusetts, New Jersey, New York, Texas, Virginia, and Washington.
+(@cit3) The population depicted in @fig-5, @fig-6, and @fig-7 contains people that searched up bullying online that live in the states with the 10 lowest percentages of Asian population.
+These states includes Arkansas, Maine, Mississippi, Montana, North Dakota, South Dakota, Alabama, West Virginia, Wyoming, and Kentucky.
+The population shown in @fig-4 shows people who searched up bullying online nationwide.
 
@@
 
-The data used in this study were pulled from reproducible package of article "Data and code for: The COVID-19 pandemic disrupted both school bullying and cyberbullying." (@cit4) According to the article, raw data were provided from Google Trends and Youth Risk Behavior Survey.
+The raw data used in this study was downloaded from the Replication Package within the article "The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying." (@cit4) According to the article, raw data was provided from Google Trends, Youth Risk Behavior Survey, U.S.
+Census Stata Population, and Burbio.
+However, the Burbio data was not provided in the Replication Package.
 
-To analysis these data, R programming language (@citeR), tidyverse (@citeTidyverse), and dplyr (@citedplyr) are used.
-ggplot2 (@citeggplot2) has been used in order to produce graphic reports.
-The use of knitr (@citeknitr) helped us to generate tables.
-Lubridate (@citelubridate) are used to reformat dates.
+Our analysis of this data was done through the R programming language (@citeR) with the tidyverse (@citeTidyverse), dplyr (@citedplyr), and knitr (@citeknitr) packages being used to clean the data.
+ggplot2 (@citeggplot2) was used to produce all the figures in this paper.
+The Lubridate (@citelubridate) package was also used to reformat dates.
 
 ## Measurements
-All the data we used is from after 2016.
-In our study, bullying data includes school bullying data and cyberbullying data.
-We measure the intensity of bullying by number of hits in one day.
-In the paper, we will refer it as search frequency.
+
+The data from Youth Risk Behavior Survey was collected from high schools throughout the United States.
+Data from Google Trends was collected by analyzing search intensity for specific topics and keywords pertaining to school bullying and cyberbullying.
+Data from the U.S.
+Census Stata Population was gathered nationwide from all civilians that participated.
+Information on the measurement of Burbio data is only available via email request, so we did not inquire.
 
@@
 
-### Bullying search dropped after COVID-19
+### Bullying and Cyberbullying Searches Decreased During COVID-19
 
@@
   labs(
-    title = "All 'Bullying' Searches in High Asian Population States",
     x = "Date",
@@
   labs(
-    title = "'Cyberbullying' Searches in High Asian Population States",
     x = "Date",
@@
 
-@fig-1 shows the number of Google hits for all 'bullying' searches in the top ten states with the highest Asian populations.
-According to Bacher-Hicks, there is a positive correlation between search intensity and frequency of victimization (Bacher-Hicks, 8).
-While unusually high peaks occur during March 2017 and 2018 with the frequency reaching 400, and the lowest clicks during summer months with numbers consistently below 200, the overall trend from 2016 to the start of the pandemic shows an overall decline.
-In 2020, when the pandemic began well known to the public, there continues to be a decline in overall search intensity.
-On average the 2020 frequency was lower than in previous years.
-This was the same time period when most schools were shut down and classes were offered online which could lead to the conclusion that bullying decreased when students were not attending classes in person.
-There is a slight rise in the summer of 2020 that is compared to the 2016 data and a reverse of the declining trends seen over the years, however, the following summer this number is reduced to the lowest number seen over the years.
-This blimp at the start of the pandemic could be a result of students being in lock down with more online time.
+\newpage
 
-@fig-2 shows the frequency of the amount of searches for "Cyberbullying".
-The naked eye test will tell you that the amount of cyberbullying searches have slightly decreased every year from 2016.
-The lowest points of the graph occur from 2020 onwards.
-The summer months are always the lowest througout the five years with a slight decrease every year.
+@fig-1 shows the number of hits for all 'bullying' searches in the top 10 states with the highest Asian population.
+According to (@cit4), there is a positive correlation between search intensity and frequency of victimization (@cit4).
+The overall trend from 2016 to the start of the pandemic shows a decline in bullying searches, despite a high peak between March 2017 and 2018.
+At the start of the pandemic, there continued to be a decline in overall search intensity.
+On average, the search intensity in 2020 was lower in comparison to previous years.
+The drop in search intensity occurred when most schools were shut down and classes swapped to online delivery.
+This leads to the conclusion that bullying decreased when students were not attending classes in person.
+
+@fig-2 shows the number of hits for all "Cyberbullying" searches.
+From the naked eye, cyberbullying searches have slightly decreased every year from 2016.
+The lowest points of the graph occured from 2020 onwards, after pandemic regulations took place.
+The summer months, when schools are closed, have the lowest search intensity within a year interval.
 The peak of the data happens in March of 2016 climbing up to 500 compared to March 2020 when it's 250.
-This is a drast difference between pre and post pandemic.
+This is a stark difference between bullying searches during and before the pandemic.
 
-Overall, the trend in search frequency and therefore, victimization, has been relatively stable with a slight decline up to the start of the pandemic and then we see further declines as a result of online learning, school closures and isolation during COVID-19.
-This graph shows there was no increase in bullying of Asian students by their peers during the pandemic in the top ten states with high Asian populations.
+Search frequency and therefore, victimization, has been slightly decreasing up to the start of the pandemic.
+From there, we see more drastic declines as a result of online learning, school closures and isolation during COVID-19.
 
-### Correlation between asian population of states and school bullying numbers
+### Correlation Between Asian Population of States and School Bullying Numbers
 
-We conducted a study to determine if there was a correlation between the increasing anti-Asian sentiment and school bullying in the United States.
+We conducted a study to determine if there was a correlation between the anti-Asian sentiment and school bullying in the United States.
 To do this, we analyzed the correlation between the search frequency for the term "school bullying" and the Asian population of each state.
-@fig-3 and @fig-4 were used to compare the search frequency of the keyword "school bullying" and the date.
+@fig-3 and @fig-4 were used to compare the search frequency of the keyword "school bullying" from 2016 onwards.
 
@@
 #| label: fig-3
-#| fig-cap: "School bullying searches in top 10 states with highest asian population"
+#| fig-cap: "School Bullying Searches in States With The Highest Asian Populations"
 #| echo: false
@@
   labs(
-    title = "'School Bullying' Searches in High Asian Population States",
     x = "Date",
@@
 The graph indicates that March 1st, 2018, had the highest number of searches for "school bullying" at over 400.
-Typically, the search frequency for "school bullying" is highest in March, and there is a significant drop in search frequency every July at approximately 150 searches when summer vacation is halfway through.
-In contrast, data for September and January are relatively closer to the average, ranging from 150 to 300.
+Typically, the search frequency for "school bullying" is highest in March, and there is a significant drop in search frequency every July at approximately 150 searches due to summer vacation.
+In contrast, data for September and January are relatively closer to the average, ranging from 150 to 300, due to those dates coinciding with the start of new school semesters.
+
+\newpage
 
@@
 #| label: fig-4
-#| fig-cap: School bullying searches nationwide
+#| fig-cap: Nationwide Search Frequencies for 'School Bullying'.
 #| echo: false
@@
   labs(
-    title = "'School Bullying' Searches Nationwide",
     x = "Date",
@@
 
-### Comparing the Top 10 Asian Population states with the Bottom 10
+### Comparing the Top 10 Asian Population States with the Bottom 10
 
@@
   labs(
-    title = "All 'Bullying' Searches in Low Asian Population States",
     x = "Date",
@@
   labs(
-    title = "'Cyberbullying' Searches in Low Asian Population States",
     x = "Date",
@@
   labs(
-    title = "'School Bullying' Searches in Low Asian Population States",
     x = "Date",
@@
 ```
-
 \newpage
 
-@fig-5, @fig-6, and @fig-7 shows the bullying searches in states with the 10 lowest percentage of Asian population.
+@fig-5, @fig-6, and @fig-7 shows, respectively, the "bullying" searches, "cyberbullying" searches and "school bullying" searches in states with the 10 lowest percentages of Asian population.
 In all three metrics, there is a decrease in bullying searches in comparison to bullying searches in the top 10 states.
@@
 # Results
-According to our previous investigations, search frequency for bullying in the top ten states with the highest Asian population slightly decreased after the start of the pandemic.
-This trend not only affected overall bullying search, but also had an impact on the search frequency trend for cyberbullying.
-Our observations indicate that the pandemic did not increase bullying in Asian American students.
-A later study that examined the correlation between the Asian population of states and school bullying numbers showed similar results.
+
+According to our findings, search frequency for bullying in the top ten states with the highest Asian population slightly decreased after the start of the pandemic.
+This trend was also applied on the search intensity for cyberbullying.
+Our observations indicate that the pandemic did not increase bullying towards Asian American students.
+The analysis that examined the correlation between the Asian population of states and school bullying numbers showed similar results.
 The study compared search intensity trends for the keyword "school bullying" in the top 10 states with the highest Asian population to nationwide data, but found no correlation between school bullying searches and the Asian population of the state.
@@
 Our study took three different angles to observe the relationship between the Asian population and search frequency in bullying, but only one of them showed a correlation.
-Therefore, future studies are needed to determine if a statistically significant correlation exists between the Asian population and bullying.
+Therefore, future studies are needed to determine if a statistically significant correlation exists between the Asian population and bullying in schools.
 It's important to continue investigating and addressing the issue of bullying in all populations and to develop effective interventions and prevention strategies to reduce its occurrence.
@@
 
-## Correlation between asian population of states and school bullying numbers
+## Correlation Between Asian Population of States and School Bullying Numbers
 
-As discussed earlier, there has been a significant increase in anti-Asian culture in the United States over the past year.
-Many may be attributed to the spread of misinformation and xenophobic rhetoric related to the COVID-19 pandemic, which has stoked hatred against Asian communities.
-Reports show that 81% of Asian adults state violence against them is increasing.
-(@cit1) Over 3800 hate-related verbal and physical assaults against Asian Americans have been reported during the pandemic.
-(@cit2)
+As discussed earlier, there has been a significant increase in anti-Asian rhetoric in the United States over the past year.
+A source of this rhetoric can be attributed to the spread of misinformation and xenophobic slander related to the COVID-19 pandemic.
+From (@cit1), 81% of Asian adults have shared an incident of violence towards them.
+Over 3800 hate-related verbal and physical assaults against Asian Americans have been reported during the pandemic (@cit2).
 
@@
 Some students may have faced racially discriminated comments, while others may have experienced exclusion or isolation from their peers.
-These reports have drawn our attention.
-We are eager to learn if there is a need to increase education and awareness among students, as well as efforts to combat racism and discrimination in all forms.
+There is a need to increase education and awareness against misinformation and xenophobia among students, as well as increasing efforts to combat racism and discrimination in all forms.
 
-In the previous section, our investigation did not reveal any correlation between the Asian population of a state and the frequency of searches related to school bullying by comparing trends in two graphs.
-While anti-Asian culture is still a large concern in the U.S., it does not seem to have a direct impact on school bullying.
-It is possible that factors like school policies, awareness campaigns, and changes in social media usage have made a positive impact on preventing discrimination and stereotyping from happening.
+While our investigation did not reveal any correlation between the Asian population of a state and the frequency of searches related to school bullying, there may have been sampling bias in play.
+From (@cit7), Asian Americans are less likely to report bullying to adults in comparison to non-Asian Americans.
+It may be the case that more Asian Americans are getting bullied, but for reasons such as culture, Asian Americans will not report bullying.
+If someone is not going to report bullying to an adult, will they search it up online or simply internalize it?
 
 ## Comparing the Top 10 Asian Population states with the Bottom 10
+
 The top 10 Asian population states experienced more school and cyber bullying than the bottom 10 Asian population states.
@@
 Anti-Asian xenophobia fueled by Covid-19 has led to an increase of hate towards Asian-Americans.
-With this in mind, Asian population does make an effect with respect to the disparity between bullying searches from the top 10 Asian population states with bullying searches from the bottom 10 Asian population states.
+With this in mind, Asian population does correlate with respect to the disparity between bullying searches from the top 10 Asian population states with bullying searches from the bottom 10 Asian population states.
 
-# Weaknesses
+However, there is more sampling bias with these data sets.
+The total population numbers for the bottom 10 Asian population states are dwarfed by the total population numbers of the top 10 Asian population states.
+So naturally, there would be less bullying searches in a state such as Montana, which has around 2.7% of California's total population.
+This is where our approach of using raw search data reaches it's limit, as we cannot draw an accurate comparison of search ratios due to the massive difference in total population numbers.
+
+## Weaknesses
 
@@
 
+## Bias
+
+Google's reported data doesn't consider the sample of users or data points.
+There is an evident sampling bias that takes occurs in this study.
+The general population can be under or overrepresented.
+It's unsure which students' searches are being used, making their age and ethnicity unclear.
+The broad population must be represented and used in our data.
+User behavior is measured by how many hits particular buzzword use.
+This measurement can be flawed as students may search other buzzwords or not use the internet to gather research on bullying and how to receive help.
+Google may only report positive trends and ignore negative ones leaving the data skewed.
+
+When on the internet, the average individual is working with information about their personal life, health, and other sensitive topics that they may not want to be shared.
+When choosing what data to report on, Google must be aware of this and careful that they're not infringing on the human right to privacy.
+There needs to be more information out there to educate the public on how their information is being used.
+The average user must be informed that their data is collected and used for reports.
+Hackers are constantly trying to steal and use innocent users' information for their gain.
+Security measures must to be implemented to protect search data from unauthorized access.
+Our dataset needs to be looked at with this in mind.
+An ethical lens must always be used when looking at people's search data to prevent discriminatory practices.
+
 # Next steps
 
-As discussed above, further studies are crucial for our studies.
+Further studies are crucial for a deeper understanding.
 Some potential steps include establishing more in-depth data analysis, adding more control variables, and conducting formal correlation tests.
@@
 Gathering more data, such as Asian population in different states, can be helpful in this regard.
+Additionally, gathering data and performing analysis on specific schools with varying Asian student populations would also be beneficial.
 The correlation coefficient can be calculated to determine the strength and direction of the relationship between the two variables.
-Besides, additional research is necessary to identify the underlying factors driving the relationship between school bullying and the Asian population.
-
-# Bias
-
-Google's reported data doesn't consider the sample of users or data points.
-There is an evident sample bias that takes occurs in this study.
-The general population can be under or overrepresented.
-It's unsure which students' searches are being used, making their age and ethnicity unclear.
-The broad population must be represented and used in our data.
-User behavior is measured by how many hits particular buzzword use.
-This measurement can be flawed as students may search other buzzwords or not use the internet to gather research on bullying and how to receive help.
-Google may only report positive trends and ignore negative ones leaving the data skewed.
-
-People have the fundamental right to privacy in all aspects of life.
-When on the internet, the average individual is dealing with information about their personal life, health, and sensitive topics they may not want to be shared.
-When choosing what data to report on, Google must be aware of this and careful that they're not impinging on the fundamental human right of privacy.
-There needs to be more information out there to educate the public on how their information is being used.
-The average citizen must be aware that their data is collected and used for reports.
-Hackers are constantly trying to infiltrate and use users' information for their gain.
-Security measures need to be introduced to protect search data from unauthorized access.
-The results an individual gets based on their search relate to their demographic and algorithm.
-Our dataset needs to be looked at with this in mind.
-An ethical lens must always be used when looking at people's search data to prevent discriminatory practices.
-
-In @fig-5, @fig-6, and @fig-7, there is sampling bias with these datasets.
-The total population numbers for the bottom 10 Asian population states are dwarfed by the total population numbers of the top 10 Asian population states.
-So naturally, there would be less bullying searches in a state like Montana, which has around 2.7% of California's total population.
-This is where our approach of using raw search data reaches it's limit, as we cannot draw an accurate comparison of search ratios due to the massive difference in total population numbers.
+Additional research is necessary to identify the underlying factors driving the relationship between school bullying and the Asian population.
 

### 2023-02-22 Outputs/Paper/paper.qmd

@@
 date-format: "D MMMM YYYY"
-abstract: "The Covid-19 pandemic incited a wave of anti-Asian hate crimes across the United States.
-This paper analyzes how school closures and the shift to online learning impacted searches about bullying in states with high and low Asian population with a comparison to pre-pandemic dates and with in-person learning.
-Results suggest that while the overall trend in bullying of high school students has been in decline nationwide between 2016-2021, with a larger drop during Covid-19, the states with high percentages of Asian populations saw a higher intensity of bullying searches when compared to states with low percentages of Asian populations over the six year period.
-These findings tell two stores: One of declining bullying trends in the US school system and one showing that anti-Asian bullying is not a result of Covid-19, but rather a sympton of a pre-existing systemic racism in our learning institutions."
+abstract: "The Covid-19 pandemic incited a wave of anti-Asian hate crimes across the United States including derogatory language in the media, random bullying, and violent, senseless murders.
+This paper analyzes how high school closures and the shift to online learning by schools throughout the pandemic, impacted incidents of bullying of Asian students compared to non Asian students when compared to pre-pandemic trends and in-person learning.
+Results suggest that while the overall trend in bullying of high school students has been in decline across all states between 2016-2021, with a larger drop during Covid-19, the states with high Asian populations saw greater incidents of bullying when compared to states with low Asian populations over the six year period.
+These findings tell both a good news story of declining bullying trends in the US school system and a highly concerning narrative that anti-Asian bullying is not a result of Covid-19, but rather an intensified awareness of pre-existing racism.
 format: pdf
@@
 
-Anti-Asian violence skyrocketed over the pandemic.
-The Center for the Study of Hate and Extremism published a report showing how anti-Asian hate crimes grew by 339% last year compared to the year before.
-These hate crimes were fueled by the pandemic, mainly occurring in highly populated urban cities like New York, San Francisco, and Los Angeles.
-The percentages of Asian hate crimes in New York rose from 30 to 133 and in San Francisco from 9 to 60.
-American culture pretends Asian-Americans face no discrimination or racism.
-There were countless examples where when the U.S.
+Anti-Asian violence skyrocketed during the Covid-19 pandemic.
+The Center for the Study of Hate and Extremism published a report showing how anti-Asian hate crimes in the United States grew by 339% from 2020 to 2021 - the height of the global crisis.
+This increase in racism, fueled by the pandemic, occurred mainly in highly populated urban cities where the population of people of Asian descent are more predominant.
+For example, the percentages of Asian hate crimes in New York rose from 30% to 133% and in San Francisco from 9% to 60%.
+American culture pretends Asian Americans face no discrimination or racism.
+There are countless examples where when the U.S.
 was faced with an economic downturn, Asian Americans were affected.

### 2023-02-22 Outputs/Paper/paper.qmd
Changed top heading of quarto

@@
 date-format: "D MMMM YYYY"
+format: 
+  pdf:
+    documentclass: article
+    geometry: margin = 1in
     abstract: "The Covid-19 pandemic incited a wave of anti-Asian hate crimes across the United States including derogatory language in the media, random bullying, and violent, senseless murders.
@@
 Results suggest that while the overall trend in bullying of high school students has been in decline across all states between 2016-2021, with a larger drop during Covid-19, the states with high Asian populations saw greater incidents of bullying when compared to states with low Asian populations over the six year period.
-These findings tell both a good news story of declining bullying trends in the US school system and a highly concerning narrative that anti-Asian bullying is not a result of Covid-19, but rather an intensified awareness of pre-existing racism.
-format: pdf
+These findings tell both a good news story of declining bullying trends in the US school system and a highly concerning narrative that anti-Asian bullying is not a result of Covid-19, but rather an intensified awareness of pre-existing racism."
 number-sections: true
@@
 
-#### use this code to graph the 3 bully datas ####
-
 sum_bully_data |> ggplot(aes(x = date, y = sum)) + 
@@
 In contrast, data for September and January are relatively closer to the average, ranging from 150 to 300, due to those dates coinciding with the start of new school semesters.
-
-\newpage
 
@@
 
-## Comparing the Top 10 Asian Population states with the Bottom 10
+## Comparing the Top 10 Asian Population States with the Bottom 10
 
@@
 
-Further studies are crucial for a deeper understanding.
-Some potential steps include establishing more in-depth data analysis, adding more control variables, and conducting formal correlation tests.
+Further studies are crucial for a deeper understanding. Some potential steps include establishing more in-depth data analysis, adding more control variables, and conducting formal correlation tests.
+
 To establish a more in-depth data analysis on school bullying and its relationship with the Asian population, we suggest introducing more factors that relate to school bullying, such as other related search terms and various social media, to provide a more complete picture of the issue.
@@
 Taking these factors into consideration can help us to identify potential areas for intervention.
+
 Furthermore, it is important to conduct formal correlation tests to determine the statistical significance of the relationship between school bullying and the Asian population.
@@
 The correlation coefficient can be calculated to determine the strength and direction of the relationship between the two variables.
+
 Additional research is necessary to identify the underlying factors driving the relationship between school bullying and the Asian population.

### 2023-02-22 Outputs/Paper/paper.qmd
Added more discussion paragraphs

@@
 
+## Bullying and Cyberbullying Searches Decreased During COVID-19
+
+The COVID-19 pandemic saw a decrease in bullying and cyberbullying searches.
+Students were no longer learning in-person, so it is natural that bullying searches would decrease.
+However, cyberbullying searches also decreased despite students spending more time online with eachother.
+There are multiple factors attributing to the decrease of cyberbullying searches during COVID-19.
+
+One factor is a steady increase of anti-bullying campaigns causing the gradual decrease in cyberbullying.
+Another factor is that outside of virtual classrooms, students are not spending time amongst their peers.
+Less exposure to one another leads to less confrontation and cyberbullying.
+One last factor is due to the digitization of student's lives during the pandemic, some students may have become desensitized to cyberbullying.
+What one student may perceive as cyberbullying, another would perceive as banter.
+The nuances of in-person communication is lost over digital communication, and these nuances lead to differences in perception.
+
 ## Correlation Between Asian Population of States and School Bullying Numbers

### 2023-02-22 Outputs/Paper/paper.qmd
Update paper.qmd

@@
 
-Anti-Asian violence skyrocketed during the Covid-19 pandemic.
-The Center for the Study of Hate and Extremism published a report showing how anti-Asian hate crimes in the United States grew by 339% from 2020 to 2021 - the height of the global crisis.
-This increase in racism, fueled by the pandemic, occurred mainly in highly populated urban cities where the population of people of Asian descent are more predominant.
-For example, the percentages of Asian hate crimes in New York rose from 30% to 133% and in San Francisco from 9% to 60%.
-American culture pretends Asian Americans face no discrimination or racism.
-There are countless examples where when the U.S.
-was faced with an economic downturn, Asian Americans were affected.
-The 1982 killing of Vincent Chin in Detroit came after the 1980-1982 Detroit recession and The Page Act of 1875, America's first immigration law that banned Chinese women after the Great Panic of 1873.
-It's safe to assume an economic horror like the pandemic would lead to hate.
-It was disconcerting reading about the different hate acts that occurred, and it was clear there needed to be culturally appropriate and accessible community safety programs.
-From the data provided, we decided to clean it, focusing on the states with an Asian population.
-There has been mainstream media coverage of anti-Asian racism but little effort toward the Asian American Youth.
+It has been widely reported in the media that discrimination and overt anti-Asian racism due to the COVID-19 pandemic is on the rise.
+By contrast, Andrew Bacher-Hicks, The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying, illustrates how the rate of bullying incidents among high schools declined during the pandemic, and discussed how these learnings can be helpful in further reducing bullying with targetted prevention and intervention strategies (Bacher-Hicks, 2020).
+Their analysis uses data from Google trends on search intensity for bullying related terms; cyberbullying, school bullying and bullying, and the times of the year bullying occurs.
+Their research proved that search intensity for bullying related terms, and state self-reported bullying rates are strongly correlated.
+
+This paper will use the initial analysis from Bachman-Hicks research to expand on their general findings to determine if anti-Asian bullying, more specifically, has followed the same overall declining trend among high school students across America.
+We will conduct our own detailed data analysis and interpretation of their results and then design three different reproductions of their data.
+First, we will examine all bullying, cyberbullying, and school bullying searches in the Top 10 Asian populated states and discuss how bullying rates changed from the pre-pandemic to post pandemic.
+Second, we will look at the top 10 Asian populated states' frequency of school bullying searches compared to the searches across the entire nation.
+Finally, we will examine the same searches in the top 10 lowest Asian populated states to gain a better understanding of how the lowest Asian populated states relate to the highest in terms of bullying search intensity.
+
+In this document, we will show that while rates of bullying have declined during the Covid-19 pandemic among high school students, they have declined less in schools located in states where people of Asian descent are the highest.
 

### 2023-02-22 Outputs/Paper/paper.qmd
Retouched introduction

@@
     geometry: margin = 1in
-    abstract: "The Covid-19 pandemic incited a wave of anti-Asian hate crimes across the United States including derogatory language in the media, random bullying, and violent, senseless murders.
+    abstract: "The COVID-19 pandemic incited a wave of anti-Asian hate crimes across the United States including derogatory language in the media, random bullying, and violent, senseless murders.
 This paper analyzes how high school closures and the shift to online learning by schools throughout the pandemic, impacted incidents of bullying of Asian students compared to non Asian students when compared to pre-pandemic trends and in-person learning.
-Results suggest that while the overall trend in bullying of high school students has been in decline across all states between 2016-2021, with a larger drop during Covid-19, the states with high Asian populations saw greater incidents of bullying when compared to states with low Asian populations over the six year period.
-These findings tell both a good news story of declining bullying trends in the US school system and a highly concerning narrative that anti-Asian bullying is not a result of Covid-19, but rather an intensified awareness of pre-existing racism."
+Results suggest that while the overall trend in bullying of high school students has been in decline across all states between 2016-2021, with a larger drop during COVID-19, the states with high Asian populations saw greater incidents of bullying when compared to states with low Asian populations over the six year period.
+These findings tell both a good news story of declining bullying trends in the US school system and a highly concerning narrative that anti-Asian bullying is not a result of COVID-19, but rather an intensified awareness of pre-existing racism."
 number-sections: true
@@
 It has been widely reported in the media that discrimination and overt anti-Asian racism due to the COVID-19 pandemic is on the rise.
-By contrast, Andrew Bacher-Hicks, The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying, illustrates how the rate of bullying incidents among high schools declined during the pandemic, and discussed how these learnings can be helpful in further reducing bullying with targetted prevention and intervention strategies (Bacher-Hicks, 2020).
-Their analysis uses data from Google trends on search intensity for bullying related terms; cyberbullying, school bullying and bullying, and the times of the year bullying occurs.
+The paper 'The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying' (@cit4) illustrated how bullying incidents among high schools nationwide declined during the pandemic, and discussed how those findings could be helpful in further reducing bullying with targeted prevention and intervention strategies.
+Their analysis used data from Google Trends on search intensity for bullying related terms; cyberbullying, school bullying and bullying, and the times of the year bullying occurs.
 Their research proved that search intensity for bullying related terms, and state self-reported bullying rates are strongly correlated.
 
-This paper will use the initial analysis from Bachman-Hicks research to expand on their general findings to determine if anti-Asian bullying, more specifically, has followed the same overall declining trend among high school students across America.
+This paper will expand upon the initial analysis from the aforementioned paper to determine if, more specifically, anti-Asian bullying has followed the same declining trend among high school students across America and if the COVID-19 pandemic has affected that trend.
 We will conduct our own detailed data analysis and interpretation of their results and then design three different reproductions of their data.
@@
 
-In this document, we will show that while rates of bullying have declined during the Covid-19 pandemic among high school students, they have declined less in schools located in states where people of Asian descent are the highest.
+Our findings will show while rates of bullying have declined during the COVID-19 pandemic among high school students, they have declined less in schools located in states where people of Asian descent are the highest.
 
@@
 From (@cit7), there has been a 70% increase in Asian American cyberbullying in 2020.
-Anti-Asian xenophobia fueled by Covid-19 has led to an increase of hate towards Asian-Americans.
+Anti-Asian xenophobia fueled by COVID-19 has led to an increase of hate towards Asian-Americans.
 With this in mind, Asian population does correlate with respect to the disparity between bullying searches from the top 10 Asian population states with bullying searches from the bottom 10 Asian population states.

### 2023-02-22 Outputs/Paper/paper.qmd
Final checks and edits

@@
 ---
-title: "The COVID-19 Pandemic's Impact on Bullying Search Intensity with respect to Asian Population"
+title: "COVID-19 Impacted Bullying Search Intensity, Asian Population Did Not"
 author: 

### 2023-02-22 Scripts/01-download_data.R

@@ -15,8 +15,6 @@ library(haven)
 #Code is manually downloaded from https://www.openicpsr.org/openicpsr/project/156901/version/V1/view
 #To download, please login with an existing ICPSR account or register a new account
 
-#raw_data <- read_dta('/Users/annie/Desktop/Spring 2023/Worlds become data/Analysis on The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying/draft/data/analysis_file.dta')
-
 #### Save data ####
 
 # Locally save the downloaded data in the project space

### 2023-02-22 Scripts/02-data_cleaning.R

@@ -11,12 +11,11 @@
 #### Workspace setup ####
 library(tidyverse)
 library(lubridate)
-# [...UPDATE THIS...]
 
 #### Clean data ####
-# [...UPDATE THIS...]
 
-##National wide data##
+##Nation wide data##
+
 #create new dataset: national schbully data 
 national_schbully_data <- state_schbully_data_raw
 national_schbully_data <- national_schbully_data |> mutate(keyword=recode(keyword, '%2Fm%2F03m50g4' = 'School Bullying'))
@@ -71,25 +70,30 @@ state_schbully_data_lowasp <- state_schbully_data_raw |> filter(dma_json_code ==
                                                        dma_json_code == 'US-ME' | dma_json_code == 'US-KY' | dma_json_code == 'US-MS' |
                                                        dma_json_code == 'US-AR', na.rm = TRUE)
 
-#Cleaning up value names so they are legible
+## Cleaning up value names so they are legible ##
+# Top 10 states with highest asian population #
 state_bully_data <- state_bully_data |> mutate(keyword=recode(keyword, '%2Fm%2F027vd9' = 'School & Cyberbullying'))
 state_cybully_data <- state_cybully_data |> mutate(keyword=recode(keyword, '%2Fm%2F07km37' = 'Cyberbullying'))
 state_schbully_data <- state_schbully_data |> mutate(keyword=recode(keyword, '%2Fm%2F03m50g4' = 'School Bullying'))
 
+# Bottom 10 states with lowest asian population #
 state_bully_data_lowasp <- state_bully_data_lowasp |> mutate(keyword=recode(keyword, '%2Fm%2F027vd9' = 'School & Cyberbullying'))
 state_cybully_data_lowasp <- state_cybully_data_lowasp |> mutate(keyword=recode(keyword, '%2Fm%2F07km37' = 'Cyberbullying'))
 state_schbully_data_lowasp <- state_schbully_data_lowasp |> mutate(keyword=recode(keyword, '%2Fm%2F03m50g4' = 'School Bullying'))
 
-#Rename dma_json_code column to State.Name for legibility
+## Rename dma_json_code column to State.Name for legibility ##
+# Top 10 states with highest asian population #
 state_bully_data <- state_bully_data |> rename(State.Name = dma_json_code)
 state_cybully_data <- state_cybully_data |> rename(State.Name = dma_json_code)
[…]

### 2023-02-22 Scripts/04-test_data.R

@@ -11,7 +11,7 @@
 #### Workspace setup ####
 library(tidyverse)
 
-
+## Reading the cleaned data CSV's ##
 sum_bully_data <- read.csv(here::here("Outputs/data/sum_bully_data.csv"))
 sum_cybully_data <- read.csv(here::here("Outputs/data/sum_cybully_data.csv"))
 sum_schbully_data <- read.csv(here::here("Outputs/data/sum_schbully_data.csv"))
@@ -25,47 +25,47 @@ cleaned_national_schbully_data <- read.csv(here::here("Outputs/data/cleaned_nati
 
 #### Test data ####
 
-#cleaned_bully_data
+#cleaned_bully_data testing
 cleaned_bully_data$ hits  |> class() == "integer"
 cleaned_bully_data$ month |> min(na.rm=TRUE) >= 0
 cleaned_bully_data$ day|> max(na.rm=TRUE) <= 31
 
-#cleaned_cybully_data
+#cleaned_cybully_data testing
 cleaned_cybully_data$ hits  |> class() == "integer"
 cleaned_cybully_data$ month |> min(na.rm=TRUE) >= 0
 cleaned_cybully_data$ day|> max(na.rm=TRUE) <= 31
 
 
-#cleaned_schbully_data
+#cleaned_schbully_data testing
 cleaned_schbully_data$ hits  |> class() == "integer"
 cleaned_schbully_data$ month |> min(na.rm=TRUE) >= 0
 cleaned_schbully_data$ day|> max(na.rm=TRUE) <= 31
 
-#cleaned_national_schbully_data
+#cleaned_national_schbully_data testing
 cleaned_national_schbully_data$ hits  |> class() == "integer"
 cleaned_national_schbully_data$ month |> min(na.rm=TRUE) >= 0
 cleaned_national_schbully_data$ day|> max(na.rm=TRUE) <= 31
 
 
-#sum_bully_data
+#sum_bully_data testing
 sum_bully_data$ X  |> class() == "integer"
 sum_bully_data$ date  |> class() == "character"
 sum_bully_data$ sum  |> class() == "integer"
 
 
-#sum_cybully_data
+#sum_cybully_data testing
 sum_cybully_data$ X  |> class() == "integer"
 sum_cybully_data$ date  |> class() == "character"
 sum_cybully_data$ sum  |> class() == "integer"
 
 
-#sum_schbully_data
+#sum_schbully_data testing
 sum_schbully_data$ X  |> class() == "integer"
[…]

### 2023-02-22 Outputs/Paper/paper.qmd
Update paper.qmd

@@
 
-Google's reported data doesn't consider the sample of users or data points.
-There is an evident sampling bias that takes occurs in this study.
-The general population can be under or overrepresented.
-It's unsure which students' searches are being used, making their age and ethnicity unclear.
-The broad population must be represented and used in our data.
-User behavior is measured by how many hits particular buzzword use.
-This measurement can be flawed as students may search other buzzwords or not use the internet to gather research on bullying and how to receive help.
+Google's reported data doesn't consider the sample of users or data points such as gender, race or age.
+There is an evident sampling bias that occurs in this study which means the general population may be under or overrepresented, which makes it challenging because the broad population must be represented and used in our data anaylsis.
+User behavior is measured by how many hits particular buzzword use which can be flawed when students search using other buzzwords or not choose to use the internet to gather research on bullying or how to receive help.
 Google may only report positive trends and ignore negative ones leaving the data skewed.
 
-When on the internet, the average individual is working with information about their personal life, health, and other sensitive topics that they may not want to be shared.
-When choosing what data to report on, Google must be aware of this and careful that they're not infringing on the human right to privacy.
-There needs to be more information out there to educate the public on how their information is being used.
-The average user must be informed that their data is collected and used for reports.
+When using the internet, the average individual is revealing information about their personal life, health, and other sensitive topics they may wish to keep private.
+When choosing data to report on, Google must carefully protect personal information and ensure the human right to privacy.
+In addition, there needs to be greater awareness and up to date information for public consumption so individuals can protect themselves.
+The average user must be informed on what data is collected and how it will be used and reported on.
 Hackers are constantly trying to steal and use innocent users' information for their gain.
 Security measures must to be implemented to protect search data from unauthorized access.
-Our dataset needs to be looked at with this in mind.
-An ethical lens must always be used when looking at people's search data to prevent discriminatory practices.
+Our dataset needs to be looked at through this ethical lens in order to prevent discriminatory practices or breech of an individuals right to privacy.
 

### 2023-02-22 Outputs/Paper/paper.qmd
Update paper.qmd

@@
 Google's reported data doesn't consider the sample of users or data points such as gender, race or age.
-There is an evident sampling bias that occurs in this study which means the general population may be under or overrepresented, which makes it challenging because the broad population must be represented and used in our data anaylsis.
+There is an evident sampling bias that occurs in this study which means the general population may be under or overrepresented, which makes it challenging because the broad population must be represented and used in our data analysis.
 User behavior is measured by how many hits particular buzzword use which can be flawed when students search using other buzzwords or not choose to use the internet to gather research on bullying or how to receive help.
@@
 Security measures must to be implemented to protect search data from unauthorized access.
-Our dataset needs to be looked at through this ethical lens in order to prevent discriminatory practices or breech of an individuals right to privacy.
+Our dataset needs to be looked at through this ethical lens in order to prevent discriminatory practices or a breach of an individuals right to privacy.
 
